### 2022-10-14 proposal.tex
Adding Proposal and citations for stat paper

% !TEX TS-program = pdflatexmk
\documentclass[12pt]{article}

%% preamble: Keep it clean; only include those you need
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}

% for space filling
\usepackage{lipsum}
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

%% meta data

\title{Proposal: Sentiment Analysis of Twitter in Relation to Fossil Fuel Stock Prices}
\author{Pranav Tavildar\\
  University of Connecticut
}

\begin{document}
\maketitle

\paragraph{Introduction}
Fossil fuel companies in the United States spends billions of dollars on advertising in order to sway public sentiment on fossil fuels. This has considerable influence on the way which the public views fossil fuels and in turn might affect stock prices.

\paragraph{Specific Aims}
The aim of this paper is to use the popular deep learning model, Long Short Term Memory(LSTM) which can be used for sentiment analysis and classification in order to perform exploratory analysis on Twitter sentiment of fossil Fuels and determine how sentiment correlates to changes in stock prices.

\paragraph{Data}
The data being used to analyze sentiment will be gathered from Twitter using the Twitter APi. Ideally I will be able to gather data mentioning the twitters of the following tip 6 oil producing corporations in the United States:
\begin{itemize}
    \item BP
    \item Chevron
    \item ConocoPhilips
    \item ExxonMobil
    \item Occidental Petroleum
    \item Shell
\end{itemize}

Then I would use historical stock from the NASDAQ to observe correlation between Twitter Sentiment and the stock prices,

\paragraph{Research Design and Methods}
LSTMs are a special type of Recurrent Neural Network that use loops in order to better handle long term dependencies. This is done through the use of forget gates and learn gates. Without getting too technical for the purpose of this proposal, the LSTM will be used for the natural language processing of the twitter sentiment in order to assign sentiment scores. Eventually these will be plotted and the data will be compared to the stock history data using Pearson-r Correlation. If strong correlation is discovered, I might try to create a model that forecasts stock price of the aforementioned companies depending on the twitter sentiment.

\paragraph{Discussion}
While LSTMs have been used before to correlate climate change on economic growth in Brazil (\cite{mele2021nature}) and sentiment analysis of climate change on twitter has been done before(\cite{dahal2019topic}) , this paper would be the first to discuss using LSTMs to analyze correlation against stock values of the companies.  As mentioned earlier, this approach will involve the use of LSTMs which perform well with time series data. There have been some papers that have been written before that applied LSTMs to forecast stock prices such as \cite{ko2021lstm} . This approach might be an interesting one to explore in this paper.

\paragraph{Conclusion}
This project will require a significant amount of development and expansion before analysis can take place but analyzing the effect of public sentiment on stock prices of fossil fuel companies can provide valuable insight into how public opinion can be used to augment or reduce the effects of climate change.

\bibliography{propreferences}
\bibliographystyle{chicago}

\end{document}

### 2022-11-15 manuscript/manuscript.tex
added file extensions and set up code directory

--- 2022-10-14 proposal.tex
@@
 
+\begin{document}
+\maketitle
+
 \paragraph{Introduction}
@@
 
-\paragraph{Specific Aims}
-The aim of this paper is to use the popular deep learning model, Long Short Term Memory(LSTM) which can be used for sentiment analysis and classification in order to perform exploratory analysis on Twitter sentiment of fossil Fuels and determine how sentiment correlates to changes in stock prices.
-
-\paragraph{Data}
-The data being used to analyze sentiment will be gathered from Twitter using the Twitter APi.
-Ideally I will be able to gather data mentioning the twitters of the following tip 6 oil producing corporations in the United States:
-\begin{itemize}
-    \item BP
-    \item Chevron
-    \item ConocoPhilips
-    \item ExxonMobil
-    \item Occidental Petroleum
-    \item Shell
-\end{itemize}
-
-Then I would use historical stock from the NASDAQ to observe correlation between Twitter Sentiment and the stock prices,
-
-\paragraph{Research Design and Methods}
-LSTMs are a special type of Recurrent Neural Network that use loops in order to better handle long term dependencies.
-This is done through the use of forget gates and learn gates.
-Without getting too technical for the purpose of this proposal, the LSTM will be used for the natural language processing of the twitter sentiment in order to assign sentiment scores.
-Eventually these will be plotted and the data will be compared to the stock history data using Pearson-r Correlation.
-If strong correlation is discovered, I might try to create a model that forecasts stock price of the aforementioned companies depending on the twitter sentiment.
-
-\paragraph{Discussion}
-While LSTMs have been used before to correlate climate change on economic growth in Brazil (\cite{mele2021nature}) and sentiment analysis of climate change on twitter has been done before(\cite{dahal2019topic}) , this paper would be the first to discuss using LSTMs to analyze correlation against stock values of the companies.
-As mentioned earlier, this approach will involve the use of LSTMs which perform well with time series data.
-There have been some papers that have been written before that applied LSTMs to forecast stock prices such as \cite{ko2021lstm} .
-This approach might be an interesting one to explore in this paper.
-
 \paragraph{Conclusion}
@@
 
-\bibliography{propreferences}
-\bibliographystyle{chicago}
+%\bibliography{propreferences}
+%\bibliographystyle{chicago}
 

### 2022-11-15 manuscript/manuscript.tex
Scraped Data and Outlining Manuscript

@@
 
-\title{Proposal: Sentiment Analysis of Twitter in Relation to Fossil Fuel Stock Prices}
+\title{Sentiment Analysis of Twitter in Relation to Fossil Fuel Stock Prices}
 \author{Pranav Tavildar\\
@@
 
-\begin{document}
-\maketitle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
 
-\paragraph{Introduction}
+\paragraph{Overview of topic}
 Fossil fuel companies in the United States spends billions of dollars on advertising in order to sway public sentiment on fossil fuels.
@@
 
-\paragraph{Conclusion}
+\paragraph{Why does it matter}
+
+\paragraph{What has been done}
+
+\section{Data Description}
+
+\paragraph{What is the data?}\
+
+\paragraph{how the economic data was obtained}
+
+\paragraph{How the twitter data was scraped}
+
+\paragraph{Exploratory data analysis}
+
+\section{Methods}
+
+\paragraph{Observed Data}
+
+\paragraph{Models}
+
+\section{Results}
+
+\section{Discussion}
+
+\paragraph{Future Directions}
 This project will require a significant amount of development and expansion before analysis can take place but analyzing the effect of public sentiment on stock prices of fossil fuel companies can provide valuable insight into how public opinion can be used to augment or reduce the effects of climate change.

### 2022-11-15 code/preliminarydatagen.py

@@ -1,0 +1,97 @@
+import snscrape.modules.twitter as sntwitter
+import pandas as pd
+from tqdm.auto import tqdm
+from time import sleep
+from datetime import date
+from datetime import timedelta
+import os
+import glob
+
+#Auxillary Function to Check for Leap Years
+def CheckLeap(Year):  
+    if((Year % 400 == 0) or  
+     (Year % 100 != 0) and  
+     (Year % 4 == 0)):   
+        return 366
+    else:  
+        return 365
+
+
+#Fetching Tweets Function
+def GrabTweets(month,year,num_tweets_per_day,query):
+
+    # Calculate Total Tweets Per Month to Collect
+    if month in [1, 3, 5, 7, 8, 10, 12]:
+        days_in_month = 31
+        total_tweets = days_in_month * num_tweets_per_day
+
+    elif month in [4, 6, 9, 11]:
+        days_in_month = 30
+        total_tweets = days_in_month * num_tweets_per_day
+
+    elif month == 2:
+        if CheckLeap(year) == 365:
+            days_in_month = 28
+            total_tweets = days_in_month * num_tweets_per_day
+        else:
+            days_in_month = 29
+            total_tweets = days_in_month * num_tweets_per_day
+
+    # Creating List to Append Tweet Data to
+    tweets_list = []
+    pbar = tqdm(total=total_tweets)
+
+    # Create Date Object
+    since = date(year,month,1).isoformat() #
+    until = date(year, month, 2).isoformat()
+    last_day = (date.fromisoformat(until)+timedelta(days=days_in_month)).isoformat()
+
+    # Counter
+    counter = 0
+
+    # Using TwitterSearchScraper to Scrape Data on Chevron in X Month in 2021 & Append Tweets to List
+    while counter != total_tweets:
+        for j in range(1):
+            for i,tweet in enumerate(sntwitter.TwitterSearchScraper('{} since:{} until:{} lang:en'.format(query, since, until)).get_items()):
+                if i >= num_tweets_per_day:
+                    since = (date.fromisoformat(since)+timedelta(days=1)).isoformat()
+                    until = (date.fromisoformat(until)+timedelta(days=1)).isoformat()
+                    break
+                tweets_list.append([tweet.date, tweet.id, tweet.content, tweet.user.username])
+                sleep(0.01)
+                counter += 1
[…]

### 2022-12-04 manuscript/manuscript.tex
Sentiment Analysis Completed
Completed Correlation Analysis and Generated Figures

@@
 
-\paragraph{Overview of topic}
-Fossil fuel companies in the United States spends billions of dollars on advertising in order to sway public sentiment on fossil fuels.
-This has considerable influence on the way which the public views fossil fuels and in turn might affect stock prices.
+%\paragraph{Overview of topic}
+	The Chevron Corporation is an America-based energy company thats has operations in over 180 countries where it has vertically integrated all operations in its supply chain such as exploration, production, refinement, chemical manufacturing, transportation, sales, marketing, and power generation.
+A lot of revenue comes from these streams but they also receive funding from government subsidies and stock revenue.
+As of when this paper was written, the Chevron Corporation has the 11th highest market capitalization with 361.57 billion dollars in stocks.
 
-\paragraph{Why does it matter}
+	As a publicly traded company, Chevron's share price is determined by supply and demand in the market.
+Generally, this is influenced by factors such as market dynamics, economic conditions and changes to economic policy.
+This information can likely be derived through public speculation and one of the best places to observe this is Twitter, the "virtual public square."
 
-\paragraph{What has been done}
+%\paragraph{Review of the Literature}
+	There exists a machine learning technique known as sentiment analysis which uses natural language processing to determine whether the sentiment towards any subject is positive or negative and assigns it a score.
+The preferred method of analyzing sequence data for most natural language processing is through the use of transformer models.
+This type of model was first introduced in the paper "Attention is all you need" \cite{}
+\paragraph{My Contribution}
+	In this paper, I seek to use a Bert-Based Transformer model to generate sentiment scores of twitter data from the year 2021 and compare with the 2021 stock prices of the Chevron Corporation (CVX) to determine whether there exists any correlation.
+\paragraph{Roadmap}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Data Description}
-
-\paragraph{What is the data?}\
-
+In order to begin sentiment analysis in order to solve this problem.
+\paragraph{What is the data?}
+There are two major methods that were used to obtain the data
 \paragraph{how the economic data was obtained}
@@
 \paragraph{Exploratory data analysis}
+yea 
+\paragraph{How its going to help answer the research question}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\paragraph{Models}
+\paragraph{The Transformer Model}
 
+\paragraph{Pearson R-Correlation}
+
+\paragraph{Why we're doing Pearson R-Correlation}
+
+\paragraph{assumptions and claims}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}
+\paragraph{Sentiment Score Analysis}
+\paragraph{Correlation}
+\paragraph{Visualizations}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion}
-
+\paragraph{Summation of Contributions of the Research}
+\paragraph{Limitations of Study}
 \paragraph{Future Directions}

### 2022-12-11 manuscript/manuscript.tex
final version of project

--- 2022-11-15 manuscript/manuscript.tex
@@
 % !TEX TS-program = pdflatexmk
-\documentclass[12pt]{article}
+\documentclass[12pt, letterpaper, titlepage]{article}
 
-%% preamble: Keep it clean; only include those you need
+\makeatletter
+\g@addto@macro\@floatboxreset\centering
+\makeatother
+
 \usepackage{amsmath}
-\usepackage[margin = 1in]{geometry}
+\usepackage{booktabs}
+\usepackage{amsthm}
 \usepackage{graphicx}
-\usepackage{booktabs}
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
 \usepackage{natbib}
+\usepackage{enumitem}
+\usepackage{float}
+\usepackage{tikz}
+\usepackage{setspace}
 
-% for space filling
-\usepackage{lipsum}
-% highlighting hyper links
-\usepackage[colorlinks=true, citecolor=blue]{hyperref}
+\usepackage[pagewise]{lineno}
+%\linenumbers*[1]
+% %% patches to make lineno work better with amsmath
+\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
+ \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
+ \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
+ \renewenvironment{#1}%
+ {\linenomath\csname old#1\endcsname}%
+ {\csname oldend#1\endcsname\endlinenomath}}%
+\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
+ \patchAmsMathEnvironmentForLineno{#1}%
+ \patchAmsMathEnvironmentForLineno{#1*}}%
+
+\AtBeginDocument{%
+ \patchBothAmsMathEnvironmentsForLineno{equation}%
+ \patchBothAmsMathEnvironmentsForLineno{align}%
+ \patchBothAmsMathEnvironmentsForLineno{flalign}%
+ \patchBothAmsMathEnvironmentsForLineno{alignat}%
+ \patchBothAmsMathEnvironmentsForLineno{gather}%
+ \patchBothAmsMathEnvironmentsForLineno{multline}%
+}
+
+% control floats
+\renewcommand\floatpagefraction{.9}
+\renewcommand\topfraction{.9}
+\renewcommand\bottomfraction{.9}
+\renewcommand\textfraction{.1}
+\setcounter{totalnumber}{50}
+\setcounter{topnumber}{50}
+\setcounter{bottomnumber}{50}
+
+\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
+\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
 
@@
 \maketitle
+\doublespace
+
+\begin{abstract}
+As a publicly traded company, the Chevron Corporation has the 11th highest market capitalization in the world with 361.57 billion dollars in traded stocks.
+There exist many social factors that contribute to this stock value but in this paper we seek to determine whether it is possible to see if any of these factors are reflected in public sentiment which can be observed in twitter.
+This is done by using a BERT transformer architecture to assign a sentiment score for each tweet and afterwords, we try to determine if there is a correlation between stock price and daily sentiment using Kendall's tau statistic.
+
+\bigskip
+\noindent{\sc Keywords}:
+BERT;
+chevron;
+twitter;
+nlp;
+sentiment analysis.
+
+\end{abstract}
 
@@
 \section{Introduction}
+\label{sec: intro}
+%\paragraph{Overview of topic}
+\paragraph{}
+	The Chevron Corporation is an America-based energy company thats has operations in over 180 countries where it has vertically integrated all operations in its supply chain such as exploration, production, refinement, chemical manufacturing, transportation, sales, marketing, and power generation.
+A lot of revenue comes from these streams but they also receive funding from government subsidies and stock revenue.
+As of when this paper was written, the Chevron Corporation has the 11th highest market capitalization with 361.57 billion dollars in traded stocks.
+	\paragraph{}
+	As a publicly traded company, Chevron's stock price is determined by supply and demand in the market.
+Generally, this is influenced by factors such as market dynamics, economic conditions and changes to economic policy.
+Through this paper, we seek to determine whether this can be predicted or determined through observing public speculation on Twitter, the "virtual public square." Being able to determine whether there exists a correlation between public sentiment and the stock price might prove as a valuable indicator for many groups such as investors, activists, and companies officials to determine how much of a correlation a change in public opinion has to the stock value.
+%\paragraph{Review of the Literature}
+\paragraph{}
+	To quantify public opinion, this paper uses a machine learning technique known as sentiment analysis \cite{medhat2014sentiment} which uses natural language processing to determine whether the sentiment towards any subject is positive or negative and assigns it a score.
+\paragraph{}
+	 Some papers in the literature use this technique in relation to analyzing activity in the stock market.
+Koosha Golmohammadi and Osmar R.
+Zaiane for instance use sentiment analysis with Twitter data to improve their Contextual Anomaly Detection(CAD) model in order to detect Market Manipulation in the United States and Canada \cite{golmohammadi2017sentiment}.
+Furthermore, Lu-Tao Zhao and Guan-Rong Zheng web text and applied Sentiment Analysis in order to do Oil Price forecasting \cite{zhao2019forecasting}.
+This concept has also been applied in order to predict one step ahead of the closing price of the stock market in Thailand using a hybrid model composed of Principle Component Analysis (PCA) for Data Processing (Dimensionality Reduction), Empirical Mode Distribution (EMD) for signal interpretation and data preprocessing, and the Long-Short-Term-Memory(LSTM) model, a specialized type of recurrent neural network for the sentiment analysis.
+\cite{srijiranon2022hybrid}
+\paragraph{}
+	While these methods have been tried and proven, as of writing this, the preferred method of analyzing sequence data for most natural language processing is through the use of transformer models.
+This type of model was first introduced in the paper "Attention is all you need" \cite{vaswani2017attention}.
+\paragraph{}
+	This model sought to improve the problems existing with the Recurrent Neural Network(RNN) model which used to be the preferred model for language processing tasks.
+Transformers have shown a lot of promise, outperforming its competitors in speed and accuracy for natural language processing tasks.
+Due to its novelty and its promising qualities, many are applying Transformers for various tasks, yet nobody has this used this approach to find out whether it is possible to find out the correlation between Twitter Sentiment and Stock prices of prominent fossil fuel corporations.
+In this paper, we specifically will focus on the Chevron Corporation (though in future iterations, we might extend this to multiple corporations in this field).
+%\paragraph{My Contribution}
+\paragraph{}
+	In this paper, we will explore using a BERT Transformer model to generate sentiment scores of twitter data from the year 2021 and compare with the 2021 stock prices of the Chevron Corporation (CVX) to determine whether there exists any significant correlation.
+\paragraph{}
+	This following is a roadmap for this study: 
+	\begin{enumerate}
+	\item Describing the Data
+	\item Explaining the Statistical Methods and the Machine Learning Concepts 
+	\item Explaining the Results of our Paper
+	\item Conducting Discussion of this Study
+	\end{enumerate}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\label{sec: datadesc}
+\section{Data Description}
+\paragraph{}
+	We use two datasets for this paper: topical twitter tweets from the year 2021 and historical stock data for CVX for the year 2021. 
+%%\paragraph{how the economic data was obtained}
+\paragraph{}
+	Gathering the Historic Stock data was the easiest part of the data collection process.
+The collection was done through Yahoo Finance's Historical Stock Data tool.
+The following is a plot of the highs and lows for the year 2021 generated using the matplotlib package for python \cite{Hunter_2007}.
 
-\paragraph{Overview of topic}
-Fossil fuel companies in the United States spends billions of dollars on advertising in order to sway public sentiment on fossil fuels.
-This has considerable influence on the way which the public views fossil fuels and in turn might affect stock prices.
+\begin{figure}[!hb]
+  \begin{center}
+  \includegraphics[width=\textwidth]{../figures/fig1.pdf}
+  \caption{Here we can see the fluctuations of the highs and lows for the stock price of CVX in 2021 with the highs labeled blue and the lows labeled yellow.
+In general both values tend to follow each other.}\label{fig:fig1}
+  \end{center}
+\end{figure}
 
-\paragraph{Why does it matter}
+\paragraph{}
+	We also used the data processing library Pandas in order to generate summary statistics as shown below:
 
-\paragraph{What has been done}
+\begin{table}[!hb]
+  \begin{center}
+    \caption{Summary Statistics for the Chevron Stock data}
+    \label{tab:table1}
+    \begin{tabular}{l|c|r} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
+      \textbf{Metrics} & \textbf{High} & \textbf{Low}\\
+      \hline
+      count & 251.000000 & 251.000000\\
+      mean & 105.196175 & 103.091753\\
+      std & 7.747654 & 7.814207\\
+      min & 85.949997 & 83.889999\\
+      25\% & 99.900002 & 97.724998\\
+      50\% & 105.080002 & 102.970001\\
+      75\% & 110.330002 & 107.969998\\
+      max & 119.339996 & 118.040001\\
+    \end{tabular}
+  \end{center}
+\end{table}
 
-\section{Data Description}
+\paragraph{}
+	The range of the stock value goes from 83.889 to 119.336 and is representative of the stock prices from January 4th, 2021 to December 30th, 2021.
+There are 251 days that the stock data was available for in 2021.
+This is because Chevron is a part of the New York Stock Exchange which is closed all day on Saturdays, Sundays and nine holidays a year.
+This was something that was taken into consideration when working with twitter data.
 
-\paragraph{What is the data?}\
+\paragraph{}
+	The twitter data was scraped using the python package snscrape \cite{justanotherarchivist_2022}.
+This is an open source library that allows for the scraping of twitter data without having to use the API.
+The code used to generate the twitter data can be found in code/datagen.py.
+In short, the process used to scrape the data was to first create some auxiliary functions for tasks such as determining how many tweets need to be gathered at a given time and create some functions to make it easier to pass in queries in the Twitter Search Scraper object.
+There are 2 things you can query for and that is by using either some topic keywords or the tweets from a specific user.
 
-\paragraph{how the economic data was obtained}
+\paragraph{}
+	For the purpose of this paper, we scraped 5 tweets a day with the topic query "Chevron Oil" from January 1st 2021 to December 31st.
+We then saved all the 1825 generated tweets as a csv and merged them with the CVX stock data on the Date axis after matching datatypes.
+This also omitted tweets which were created when the stock market was closed in order to simplify the analysis.
+Using this we were able to perform sentiment and calculate correlation.
 
-\paragraph{How the twitter data was scraped}
-
-\paragraph{Exploratory data analysis}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\label{sec: methods}
 \section{Methods}
 
-\paragraph{Observed Data}
+\paragraph{}
+	The two primary methods we're going to be using in this paper for data analysis would be sentiment analysis using transformers and Kendall rank correlation.
+We will now go into details of how both work.
 
-\paragraph{Models}
+\paragraph{The Transformer Model}
+	As we mentioned earlier, Transformers have shown a lot of promise, outperforming its competitors in speed and accuracy for natural language processing tasks.
+The BERT model seems to be particularly well suited for tasks of sentiment analysis.
+Transformers work based on the concept of "attention" which was introduced in "Attention is all you need" \cite{vaswani2017attention} is a deep learning model that was first used for computer vision models.
+Transformers create differential weights signaling which words in a sentence are the most critical to further process.
+This allows them to "forget"  irrelevant information which would use other critical resources.
 
+\begin{figure}[H]
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+%Rounded Rect [id:dp4434986972980839] 
+\draw   (100,43.8) ..
+controls (100,32.76) and (108.95,23.8) ..
+(120,23.8) -- (261,23.8) ..
+controls (272.05,23.8) and (281,32.76) ..
+(281,43.8) -- (281,103.8) ..
+controls (281,114.85) and (272.05,123.8) ..
+(261,123.8) -- (120,123.8) ..
+controls (108.95,123.8) and (100,114.85) ..
+(100,103.8) -- cycle ;
+%Rounded Rect [id:dp8739677930569794] 
+\draw   (359,68.2) ..
+controls (359,52.52) and (371.72,39.8) ..
+(387.4,39.8) -- (472.6,39.8) ..
+controls (488.28,39.8) and (501,52.52) ..
+(501,68.2) -- (501,168.4) ..
+controls (501,184.09) and (488.28,196.8) ..
+(472.6,196.8) -- (387.4,196.8) ..
+controls (371.72,196.8) and (359,184.09) ..
+(359,168.4) -- cycle ;
+%Curve Lines [id:da9359490056283244] 
+\draw    (282,73) .. controls (362,56.8) and (275,143.8) .. (359,124.8) ;
+%Straight Lines [id:da03881732608220867] 
+\draw    (78,72.8) -- (101,73) ;
+%Straight Lines [id:da6091063106538472] 
+\draw    (500,120.8) -- (523,121) ;
+%Straight Lines [id:da19347919375178857] 
+\draw    (431,215.8) -- (431,199.8) ;
+% Text Node
+\draw (161,65) node [anchor=north west][inner sep=0.75pt]   [align=left] {Encoder};
+% Text Node
+\draw (398,103) node [anchor=north west][inner sep=0.75pt]   [align=left] {Decoder};
+% Text Node
+\draw (42,63) node [anchor=north west][inner sep=0.75pt]   [align=left] {Input};
+% Text Node
+\draw (524,112) node [anchor=north west][inner sep=0.75pt]   [align=left] {Output};
+% Text Node
+\draw (408,219) node [anchor=north west][inner sep=0.75pt]   [align=left] { Output Probabilites};
+\end{tikzpicture}
+\caption{In this figure we can observe a very simplified version of the Transformer model with its two major components, the encoder and the decoder.
+The encoder processes a text input through a stack of transformer layers.
+In some situations, another set of transformer layers, the decoder, can be used to predict a target output.
+Note that this model might be used for a task such as language translation.\cite{devlin2018bert}}\label{fig:fig2}
+\end{figure}
+
+\paragraph{}
+For our Sentiment Analysis we will be using Bidirectional Encoder Representations from Transformers(BERT), a transformer model created by Google which serves as a many-in-one tool for the most common Natural Language Processing Tasks:
+\begin{itemize}
+    \item Sentiment Analysis
+    \item Text Classification
+    \item Chatbots
+    \item Text Extraction
+    \item Machine Translation
+    \item Text Summarization
+    \item Market Intelligence
+    \item Auto-Correct
+    \item Intent Classification
+    \item Urgency Detection
+    \item Speech Recognition
+\end{itemize}
+
+\paragraph{}
+This model was initially trained on Wikipedia and Google’s BooksCorpus which contain 2,500,000,000 words and 800,000,000 words respectively.
+Training of BERT was completed over a period of 4 days using 64 Tensor Processing Units running in parallel.
+With this much data, it is able to understand context clues making it a very effective model for the purposes of sentiment analysis.
+
+\paragraph{}
+We will be specifically using BERT-base which is a version of BERT with 12 transformation layers, and 768 Hidden Layers.\cite{muller_2022} This is more reasonable for the task we have at hand and we will implement this using the transformers package.
+
+\paragraph{Kendall Correlation}
+Kendall's Rank Tau coefficient is one of the most widely used methods for determining correlations between two variables that have a monotonic relationship.
+Before describing the equation, it is worth noting the assumptions of the Kendall Tau Correlation Test.
+\begin{enumerate}
+	\item The data must be continuous. This means that the data must be numeric and may not contain any interruptions.
+	\item The data must be monotonic meaning that it has to be entirely increasing or decreasing
+	\end{enumerate}
+It is also important to understand the concept of concordant and discordant pairs before revealing the equation.
+Let  $(x_{1},y_{1}),...,(x_{n},y_{n}) $ and $(x_{1},y_{1}),...,(x_{n},y_{n})$ be a set of observations of the joint random variables X and Y.
+If a pair $(x_{i},y_{i})$ and $(x_{j},y_{j})$ is concordant, then their sort order agrees.
+In other words, either both $ x_{i}>x_{j}$ and  $y_{i}>y_{j}$ holds or both $x_{i}<x_{j}$ and $y_{i}<y_{j}$.
+Otherwise, the pair is said to be discordant.
+
+\paragraph{}
+\begin{equation}
+  \label{eq:Kendall}
+   \tau = \frac{a-b}{a + b}
+\end{equation}
+
+\paragraph{}
+Where a is the number of concordant pairs and b is the number of discordant pairs. $\tau$ is a value in [0,1] where 0 indicates no correlation and 1 indicates perfect correlation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\label{sec: results}
 \section{Results}
+\paragraph{}
+The sentiment analysis took approximately 12 minutes to run and the data generated created 3 new columns in the working dataframe: sentiment, label, and score.
+Score is a numeric value from the range [0,1] where the higher the score the more confident the sentiment analyzed is correct.
+This variable is one of interest to us since we want to use it to measure correlation with highs of the stock market The summary statistics listed the following:
 
+\begin{table}[!hb]
+  \begin{center}
+    \caption{Summary Statistics for the Sentiment Analysis of Tweets}
+    \label{tab:table2}
+    \begin{tabular}{l|c|r} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
+      \textbf{Metrics} & \textbf{High} \\
+      \hline
+      count & 1160 \\
+      mean & 0.960652 \\
+      std & 0.086946 \\
+      min & 0.500485 \\
+      25\% & 0.9740872 \\
+      50\% & 0.992183 \\
+      75\% & 0.997086 \\
+      max & 0.999799 \\
+    \end{tabular}
+  \end{center}
+\end{table}
+
+\paragraph{}
+To calculate correlation, we must make sure that the fundamental assumptions are satisfied.
+The data is continuous and monotonic so we can proceed with Kendall's correlation.
+We used pandas to calculate Kendall's correlation.
+The following is a heat map of the correlation plotted using the seaborn package for python \cite{Waskom2021}.
+
+\begin{figure}[H]
+  \begin{center}
+  \includegraphics[width=\textwidth]{../figures/fig2.pdf}
+  \caption{Here we can observe the correlation between sentiment score and stock high price. The value is -0.009447. }\label{fig:fig2}
+  \end{center}
+\end{figure}
+
+Given that the correlation it is negative, this indicates that there is a very minor inverse relationship between score and stock price.
+But given how low it is, this result is practically negligible and it appears that there is almost 0 correlation between the variables we are measuring.
+This indicates a lot of revision being needed for the data and methods of analysis in this paper.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\label{sec: discussion}
 \section{Discussion}
+\paragraph{}
+	As mentioned before, this paper is the first one to take the approach of using Transformers to determine whether it is possible to find out the correlation between Twitter Sentiment and Stock prices of prominent fossil fuel corporations.
+In summary, this paper accomplished this task through the following:
+\begin{itemize}
+    \item Introducing some background behind the Chevron Corporation and Sentiment Analysis as a Practice.
+    \item Describing the data and the methods by which the data was obtained.
+    \item Describing the methods behind the sentiment analysis and correlation derivation
+    \item Describing the results
+    Through code and analysis, we were eventually did get a correlation coefficient score of -0.009447 which is very low based on what was expected indicating that there is very little correlation between twitter sentiment and stock price.
 
-\paragraph{Future Directions}
-This project will require a significant amount of development and expansion before analysis can take place but analyzing the effect of public sentiment on stock prices of fossil fuel companies can provide valuable insight into how public opinion can be used to augment or reduce the effects of climate change.
+\end{itemize}
+\paragraph{}
+	In its current state, this study is intended to work as a proof of concept to determine whether it is possible to create a data processing pipeline which could be used to assign sentiment scores and connect it to stock time series data so the results determined through this preliminary paper should not be taken as a final answer to the research question that were posed.
+This study had many limitations which can be addressed to get a more accurate answer.
 
-%\bibliography{propreferences}
-%\bibliographystyle{chicago}
+	For instance the transformer pipeline model that was used handled cleaning and preprocessing automatically, this might have lead to improper tokenization which allowed for incorrect sentiment analysis.
+The 18th tweet in merged.csv reads
+
+	"Richmond Mayor Tom Butt was publicly optimistic about a Chevron oil refinery spill. In private he took on a much different tone."
+
+	This was labelled as positive by BERT but in actuality this is a negative tweet.
+\paragraph{}
+	To avoid instances like this we could also use more terms for the tweet querying such as a specific event such as an oil spill or possibly the stock indicator itself.
+
+\paragraph{}
+The major things to address as next steps are improving the data quality, quantity and analysis.
+I will also explore using the twitter API to gather tweets instead of using snscrape since the API is the prefered method of gathering tweets in professional contexts and this opens data gathering up to many more possibilities with new methods and feature information that could be gathered using the API query feature.
+Having more tweets per day is also beneficial in improving the quality of analysis.
+
+\paragraph{}
+Furthermore, using different data and methods would allow us to possibly create a model that can forecast stock pricing if the correlation is strong enough.
+This would be done in a manner similarly to \cite{zhao2019forecasting}.
+
+This project will require much more development and expansion before a conclusion  can be determined but analyzing the effect of public sentiment on stock prices of fossil fuel companies can provide valuable insight into how public opinion can be used to augment or reduce the effects of climate change.
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bibliographystyle{chicago}
+\bibliography{references}
 

### 2023-01-31 manuscript/manuscript.tex
Fixed some language and obtained quote tweets

@@
 \paragraph{}
-	To quantify public opinion, this paper uses a machine learning technique known as sentiment analysis \cite{medhat2014sentiment} which uses natural language processing to determine whether the sentiment towards any subject is positive or negative and assigns it a score.
+	To quantify public opinion, this paper uses a machine learning technique known as sentiment analysis \citep{medhat2014sentiment} which uses natural language processing to determine whether the sentiment towards any subject is positive or negative and assigns it a score.
 \paragraph{}
@@
 Koosha Golmohammadi and Osmar R.
-Zaiane for instance use sentiment analysis with Twitter data to improve their Contextual Anomaly Detection(CAD) model in order to detect Market Manipulation in the United States and Canada \cite{golmohammadi2017sentiment}.
-Furthermore, Lu-Tao Zhao and Guan-Rong Zheng web text and applied Sentiment Analysis in order to do Oil Price forecasting \cite{zhao2019forecasting}.
+Zaiane for instance use sentiment analysis with Twitter data to improve their Contextual Anomaly Detection(CAD) model in order to detect Market Manipulation in the United States and Canada \citep{golmohammadi2017sentiment}.
+Furthermore, Lu-Tao Zhao and Guan-Rong Zheng web text and applied Sentiment Analysis in order to do Oil Price forecasting \citep{zhao2019forecasting}.
 This concept has also been applied in order to predict one step ahead of the closing price of the stock market in Thailand using a hybrid model composed of Principle Component Analysis (PCA) for Data Processing (Dimensionality Reduction), Empirical Mode Distribution (EMD) for signal interpretation and data preprocessing, and the Long-Short-Term-Memory(LSTM) model, a specialized type of recurrent neural network for the sentiment analysis.
-\cite{srijiranon2022hybrid}
+\citep{srijiranon2022hybrid}
 \paragraph{}
 	While these methods have been tried and proven, as of writing this, the preferred method of analyzing sequence data for most natural language processing is through the use of transformer models.
-This type of model was first introduced in the paper "Attention is all you need" \cite{vaswani2017attention}.
+This type of model was first introduced in the paper "Attention is all you need" \citep{vaswani2017attention}.
 \paragraph{}
@@
 \paragraph{}
-	This following is a roadmap for this study: 
-	\begin{enumerate}
-	\item Describing the Data
-	\item Explaining the Statistical Methods and the Machine Learning Concepts 
-	\item Explaining the Results of our Paper
-	\item Conducting Discussion of this Study
-	\end{enumerate}
+	This following is a roadmap for this study: 1) Describing the Data, 2) Explaining the Statistical Methods and the Machine Learning Concepts, 3) Explaining the Results of our Paper, 4) Conducting Discussion of this Study
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The collection was done through Yahoo Finance's Historical Stock Data tool.
-The following is a plot of the highs and lows for the year 2021 generated using the matplotlib package for python \cite{Hunter_2007}.
+The following is a plot of the highs and lows for the year 2021 generated using the matplotlib package for python \citep{Hunter_2007}.
 
@@
 \paragraph{}
-	The twitter data was scraped using the python package snscrape \cite{justanotherarchivist_2022}.
+	The twitter data was scraped using the python package snscrape \citep{justanotherarchivist_2022}.
 This is an open source library that allows for the scraping of twitter data without having to use the API.
@@
 The BERT model seems to be particularly well suited for tasks of sentiment analysis.
-Transformers work based on the concept of "attention" which was introduced in "Attention is all you need" \cite{vaswani2017attention} is a deep learning model that was first used for computer vision models.
+Transformers work based on the concept of "attention" which was introduced in "Attention is all you need" \citep{vaswani2017attention} is a deep learning model that was first used for computer vision models.
 Transformers create differential weights signaling which words in a sentence are the most critical to further process.
@@
 In some situations, another set of transformer layers, the decoder, can be used to predict a target output.
-Note that this model might be used for a task such as language translation.\cite{devlin2018bert}}\label{fig:fig2}
+Note that this model might be used for a task such as language translation.\citep{devlin2018bert}}\label{fig:fig2}
 \end{figure}
@@
 \paragraph{}
-We will be specifically using BERT-base which is a version of BERT with 12 transformation layers, and 768 Hidden Layers.\cite{muller_2022} This is more reasonable for the task we have at hand and we will implement this using the transformers package.
+We will be specifically using BERT-base which is a version of BERT with 12 transformation layers, and 768 Hidden Layers.\citep{muller_2022} This is more reasonable for the task we have at hand and we will implement this using the transformers package.
 
@@
 We used pandas to calculate Kendall's correlation.
-The following is a heat map of the correlation plotted using the seaborn package for python \cite{Waskom2021}.
+The following is a heat map of the correlation plotted using the seaborn package for python \citep{Waskom2021}.
 
@@
 Furthermore, using different data and methods would allow us to possibly create a model that can forecast stock pricing if the correlation is strong enough.
-This would be done in a manner similarly to \cite{zhao2019forecasting}.
+This would be done in a manner similarly to \citep{zhao2019forecasting}.
 

### 2023-01-31 code/poc.py

@@ -1,0 +1,18 @@
+import snscrape.modules.twitter as sntwitter
+import pandas as pd
+from tqdm.auto import tqdm
+from time import sleep
+from datetime import date
+from datetime import timedelta
+import os
+import glob
+
+tweets_list = []
+for i,tweet in enumerate(sntwitter.TwitterSearchScraper('CVX until:2023-01-28 since:2023-01-25 lang:en').get_items()): #declare a username 
+    if i>20: #number of tweets you want to scrape
+        break
+    tweets_list.append([tweet.date, tweet.id, tweet.content, tweet.quoteCount, tweet.retweetCount]) #declare the attributes to be returned
+
+df = pd.DataFrame(tweets_list,columns=["Date","ID","Content","QuoteCount","Retweets"])
+
+df.to_csv('popularitymatrix.csv')

### 2023-04-04 code/Thesis_R_Code.Rmd
Reformatted R Code to Rmd. Edited methods section

---
title: "Thesis_R_Code"
author: "Pranav Tavildar"
date: "2023-04-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Libraries

```{r}
library(rugarch)
library(readr)
library(forecast)
library(tseries)
library(garchx)
library(TSA)
```

## Loading Data and Calculating Returns
```{r}
stock_data <- read.csv("/Users/pranavtavildar/Desktop/Senior-Thesis/data/CVX_stock_data.csv")
returns <- diff(log(stock_data$Close))
plot(ts(returns))
```

## Here we use auto.arima to select the best arima model
```{r}
arma_model <- auto.arima(returns,  max.D = 0, max.d = 0)
arma_model
```

## Here, we are doing Garch where the order is (1,1) and we apply it to the arima model selected by auto.arima
```{r}
garch_spec <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1,1)), mean.model = list(armaOrder = c(0,0)))
garch_model2 <- ugarchfit(garch_spec, data = returns)
summary(garch_model2)
show(garch_model2)
```

t value of beta 1 proves that the p value is non significant

## Alternative Garch implementation gives us the same result
```{r}
garch_model <- garch(returns)
garch_model

summary(arma_model)
residuals_garch <- residuals(garch_model)
plot(residuals_garch)
```

## Adding Exogenous Variable (sentiment score)
```{r}
sentiment_df <- read.csv("/Users/pranavtavildar/Desktop/Senior-Thesis/data/daily_sentiments.csv", header = TRUE)
str(sentiment_df)
str(returns)
sentiment_df = sentiment_df[-1,]
```

## Fitting Arima Model to the new data
```{r}
arma_model <- auto.arima(returns,  max.D = 0, max.d = 0)
arma_model

sentiment_arma_model <- auto.arima(sentiment_df$sentiment,  max.D = 0, max.d = 0)
sentiment_arma_model
```

## Adjusting Scale for Garchx
```{r}
adj_sentiment <- sentiment_df$sentiment/100
```

## Running arimax and Garchx
```{r}
###armax
exarma_model <- arimax(x = returns, xreg = sentiment_df$sentiment, order= c(1,0,1))
exarma_model

###garchx
centered_returns <- scale(returns, center = TRUE, scale = FALSE)
garchx_model <- garchx(centered_returns, xreg=adj_sentiment, order = c(1,1), initial.values = c(coef(garch_model),0))
garchx_model
```

## Repeating Process with Weighted Sentiment Score
```{r}
### weighted sentiment score 
weighted_df <- read.csv("/Users/pranavtavildar/Desktop/Senior-Thesis/data/weighted_daily_sentiments.csv", header = TRUE)
str(weighted_df)
str(returns)
weighted_df = weighted_df[-1,]

###armax
exarma_model <- arimax(x = returns, xreg = weighted_df$weighted_sentiment)
exarma_model

###garchx
garchx_model <- garchx(returns, xreg=sentiment_df$weighted_sentiment)
summary(garchx_model)
```

### 2023-04-04 manuscript/manuscript.tex
Reformatted R Code to Rmd. Edited methods section

@@
 There exist many social factors that contribute to this stock value but in this paper we seek to determine whether it is possible to see if any of these factors are reflected in public sentiment which can be observed in twitter.
-This is done by using a BERT transformer architecture to assign a sentiment score for each tweet and afterwords, we try to determine if there is a correlation between stock price and daily sentiment using Kendall's tau statistic.
+This is done by using a BERT transformer architecture to assign a sentiment score for each tweet and afterwords, we try to determine if there is a correlation between stock price and daily sentiment using an ARMA GARCH Model.
 
@@
 
-\paragraph{}
-	The two primary methods we're going to be using in this paper for data analysis would be sentiment analysis using transformers and Kendall rank correlation.
-We will now go into details of how both work.
+\subsection{Data Collection}
+Twitter data related to the Chevron Corporation was collected using web scraping techniques.
+Specifically, tweets containing the term "CVX" were extracted from Twitter using the topic selection method provided by the snscrape\citep{justanotherarchivist_2022} Python wrapper.
+The tweets were collected for a period of 2 years, from January 1, 2021 to December 31, 2022 with 10 tweets being collected each day.
 
+\subsection{Sentiment Analysis}
 \paragraph{The Transformer Model}
@@
 \paragraph{}
-For our Sentiment Analysis we will be using Bidirectional Encoder Representations from Transformers(BERT), a transformer model created by Google which serves as a many-in-one tool for the most common Natural Language Processing Tasks:
-\begin{itemize}
-    \item Sentiment Analysis
-    \item Text Classification
-    \item Chatbots
-    \item Text Extraction
-    \item Machine Translation
-    \item Text Summarization
-    \item Market Intelligence
-    \item Auto-Correct
-    \item Intent Classification
-    \item Urgency Detection
-    \item Speech Recognition
-\end{itemize}
+We will be utilizing Bidirectional Encoder Representations from Transformers (BERT) for our sentiment analysis.
+BERT is a transformer model developed by Google that can perform multiple Natural Language Processing tasks such as sentiment analysis, text classification, chatbots, text extraction, machine translation, text summarization, market intelligence, auto-correct, intent classification, urgency detection, and speech recognition.
 
@@
 \paragraph{}
-We will be specifically using BERT-base which is a version of BERT with 12 transformation layers, and 768 Hidden Layers.\citep{muller_2022} This is more reasonable for the task we have at hand and we will implement this using the transformers package.
+We will be specifically using BERT-base which is a version of BERT with 12 transformation layers, and 768 Hidden Layers.\citep{muller_2022} This is more reasonable for the task we have at hand and we will implement this using the Hugging Face transformers package.
+For each day, the average sentiment score of all tweets was calculated.
+Sentiment scores range from -1 to 1, where -1 represents a very negative sentiment and 1 represents a very positive sentiment.
 
-\paragraph{Kendall Correlation}
-Kendall's Rank Tau coefficient is one of the most widely used methods for determining correlations between two variables that have a monotonic relationship.
-Before describing the equation, it is worth noting the assumptions of the Kendall Tau Correlation Test.
-\begin{enumerate}
-	\item The data must be continuous. This means that the data must be numeric and may not contain any interruptions.
-	\item The data must be monotonic meaning that it has to be entirely increasing or decreasing
-	\end{enumerate}
-It is also important to understand the concept of concordant and discordant pairs before revealing the equation.
-Let  $(x_{1},y_{1}),...,(x_{n},y_{n}) $ and $(x_{1},y_{1}),...,(x_{n},y_{n})$ be a set of observations of the joint random variables X and Y.
-If a pair $(x_{i},y_{i})$ and $(x_{j},y_{j})$ is concordant, then their sort order agrees.
-In other words, either both $ x_{i}>x_{j}$ and  $y_{i}>y_{j}$ holds or both $x_{i}<x_{j}$ and $y_{i}<y_{j}$.
-Otherwise, the pair is said to be discordant.
+\subsection{ARMA-GARCH Modeling}
+The daily returns for Chevron's stock (CVX) were obtained from calculating as the daily logarithmic difference of the closing prices.
+ARMA-GARCH modeling was then performed to investigate the relationship between the daily returns and the sentiment scores.
 
-\paragraph{}
-\begin{equation}
-  \label{eq:Kendall}
-   \tau = \frac{a-b}{a + b}
-\end{equation}
+First, an ARMA model was selected for the returns using the \texttt{auto.arima} function in the forecast package in R.
+The \texttt{max.D} and \texttt{max.d} parameters were set to 0 to avoid differencing in the ARMA model.
 
-\paragraph{}
-Where a is the number of concordant pairs and b is the number of discordant pairs. $\tau$ is a value in [0,1] where 0 indicates no correlation and 1 indicates perfect correlation.
+Next, a GARCH model was fitted to the ARMA residuals using the \texttt{ugarchfit} function in the rugarch package in R.
+The sGARCH model was used for the variance with an order of (1,1) and the mean was modeled using the ARMA model selected earlier.
+
+To investigate the impact of sentiment on stock returns, an ARIMAX model was fitted to the returns using the \texttt{arimax} function in the TSA package in R.
+The daily sentiment scores were included as an exogenous variable.
+An ARIMAX model was also fitted to the sentiment scores using the \texttt{auto.arima} function in the forecast package in R.
+
+Finally, a GARCHX model was fitted to the returns with sentiment scores using the \texttt{garchx} function in the garchx package in R.
+The order was set to (1,1), and the initial values for the GARCH coefficients were taken from the ARMA-GARCH model.
+
+For further analysis, a weighted sentiment score was calculated by assigning a weight to each sentiment score based on the number of tweets collected for that day.
+The weighted sentiment score was then used as an exogenous variable in the ARIMAX and GARCHX models, and the results were compared to those obtained using the unweighted sentiment score.
 

### 2023-04-20 FrontiersPoster/poster.Rmd
Draft of Thesis and Poster worked

---
title: "Correlation Analysis of Twitter Sentiment and Fossil Fuel Stock Valuation"
author:
  - name: Pranav Tavildar
    affil: 1
  - name: Jun Yan
    affil: 1
affiliation:
  - num: 1
    address: Department of Statistics, University of Connecticut
column_numbers: 3
poster_height: "36in"
poster_width: "40in"
logoleft_name: "uconn-wordmark-single-white.png"
logoright_name: "uconn-wordmark-single-white.png"
primary_colour: "#000E2F"
secondary_colour: "#FFFFFF"
sectitle2_textcol: "#000E2F"
body_textsize: "30pt"
sectitle_textsize: "50pt"
column_margins: "0.2in"
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: references.bib

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{css, echo=FALSE}
#title {
  padding-top: 1.5cm;
  padding-bottom: 1.5cm;
}

.title_container {
  height: calc(38in * 0.13);
}

img {
  margin-top: 0cm;
}
```

# 1. Abstract
Using natural language processing techniques and modified time-series modeling, this paper aims to establish a methodology to test whether twitter sentiment is informative in predicting stock price movement and its volatility for the Chevron Corporation(CVX). The following QR Code links to the file repository.

<div style="text-align: center;">
  <img width="50%" src="figures/qr.png" alt="Image">
</div>
<!-- <image width="50%" src="figures/qr.png" class="center"/> -->

# 2. Introduction
This paper aims to determine if there is a correlation between public sentiment on Twitter and Chevron's stock price. It will use a machine learning technique called sentiment analysis with a BERT Transformer model to analyze Twitter data from January 1st, 2021-December 31st, 2022 and compare it with Chevron's stock prices in the same years. The paper includes sections on data collection, statistical methods, results, and further discussion.

# 3. Methods

## 3.1. Data Collection
<!-- Twitter data related to the Chevron Corporation was collected using web scraping techniques. Specifically, tweets containing the term ”CVX” were extracted from Twitter using the topic selection method provided by the snscrape Python wrapper @snscrape. The tweets were collected for a period of 2 years, from January 1, 2021 to December 31, 2022 with 10 tweets being collected each day. Financial stock data was also collected for the Chevron corporation within this same period. For the purposes of this paper, returns obtained by taking the log difference of the daily closing prices.  -->
- Twitter data collected for Chevron Corporation using web scraping and the snscrape Python wrapper[@justanotherarchivist_2022].
- Tweets containing "CVX" extracted from Twitter for 2-year period: January 1, 2021 to December 31, 2022, 10 tweets collected per day.
- Financial stock data also collected for Chevron for same period.
- Returns calculated by taking log difference of daily closing prices for analysis.

<div style="text-align: center;">
  <img width="70%" src="figures/returnsplot.png" alt="Image">
</div>

## 3.2. Sentiment Analysis
<!-- The sentiment analysis involved utilizing Hugging Face's BERT transformer architecture to assign sentiment scores to each tweet. Using self-attention mechanisms such as encoders and decoders to process input sequences in parallel, transformers can capture long-range dependencies and relationships between words, making it highly effective for tasks such as language translation and natural language processing, and for our purpose, sentiment analysis. -->
- Hugging Face's BERT transformer architecture used.[@huggingface2023]
- Self-attention mechanisms (encoders and decoders) were used to process input sequences in parallel.
- Transformers use attention are very effective for capturing long-range dependencies and relationships between words.Conceptualized in [@vaswani2017attention]
- BERT used for sentiment analysis in this study.[@devlin2018bert]

<div style="text-align: center;">
  <img width="100%" src="figures/transformerdiagram.png" alt="Image">
</div>

## 3.3. ARMA-GARCH
ARMA-GARCH is a time-series modeling approach that combines Autoregressive Moving Average (ARMA) models for capturing time-dependent patterns with Generalized Autoregressive Conditional Heteroskedasticity (GARCH) models for modeling time-varying volatility.

# 4. Results
<!-- Within the specified period of January 1st, 2021-December 31st, 2022, we collected 10 tweets a day. We then selected data for the 502 dates that the stock market was open and averaged the sentiment scores for each day. The following histogram shows the normal distribution observed in the data. -->

<!-- <image width="100%" src="poster_files/figures/sentimenthist.png"/> -->

<!-- After obtaining the sentiment score as daily sentiment we created an ARMA-GARCH model first only using the daily sentiment and then comparing to an ARMA-GARCH model with daily sentiment as an exogenous variable. The ARMA part of this technique, models the autocorrelation and moving average patterns in the data and GARCH models the volatility or conditional heteroskedasticity of the data. To determine whether daily sentiment, the exogenous variable has any effect on the model, we conducted the Likelihood ratio test. The p-value associated with the likelihood ratio test that we used was above which was our chosen significance value of 0.05, so we could not reject that the null hypothesis that the exogenous variable has no effect on the model. We tried this same technique by applying a weight to the sentiment score and obtained similar results. -->
- Data selected for 502 dates when stock market was open.
- 10 Sentiment scores calculated and averaged for each day.

Histogram showing normal distribution observed in the data.

<div style="text-align: center;">
  <img width="100%" src="figures/sentimenthist.png" alt="Image">
</div>

- Conducted Likelihood ratio test to determine effect of daily sentiment as exogenous variable.
- Chosen significance value: 0.05.
- Likelihood ratio test gave a p-value above 0.05, indicating no significant effect of exogenous variable on the model.
- A weighted sentiment was also tried and similar results were concluded.

# 5. Conclusion

## 5.1. Possible Expansions
- Increase sample size for more robust analysis.
- Test for causality using techniques like the Granger causality test.
- Conduct meta-analysis of multiple companies in the fossil fuel industry for broader insights.

## 5.2. Takeaway
While both weighted and unweighted sentiment score might not have been effective in predicting stock price movement and volatility of CVX, this paper establishes a novel methodology that can be applied to determine whether twitter sentiment is informative in predicting stock movement and volatility across many industries and sectors.

# 6. References

### 2023-04-20 code/Thesis_R_Code.Rmd
Draft of Thesis and Poster worked

@@
 
-```{r}
+```{r,results='hide'}
 library(rugarch)
@@
 returns <- diff(log(stock_data$Close))
-plot(ts(returns))
+plot(ts(returns), main = "Returns", xlab = "Date", ylab = "Returns")
+output_path <- "/Users/pranavtavildar/Desktop/Senior-Thesis/FrontiersPoster/FrontiersPoster_files/poster_files/figures/returnsplot.png"
+
+png(file = output_path)
+dev.off()
+
 ```
@@
 sentiment_df = sentiment_df[-1,]
+hist(sentiment_df$sentiment, main = "Sentiment Distribution", xlab = "Sentiment Score", ylab = "Frequency")
+
+output_path <- "/Users/pranavtavildar/Desktop/Senior-Thesis/FrontiersPoster/FrontiersPoster_files/poster_files/figures/sentimenthist.png"
+
+png(file = output_path)
+dev.off()
+
 ```

### 2023-04-20 manuscript/manuscript.tex
Draft of Thesis and Poster worked

@@
 As a publicly traded company, the Chevron Corporation has the 11th highest market capitalization in the world with 361.57 billion dollars in traded stocks.
-There exist many social factors that contribute to this stock value but in this paper we seek to determine whether it is possible to see if any of these factors are reflected in public sentiment which can be observed in twitter.
-This is done by using a BERT transformer architecture to assign a sentiment score for each tweet and afterwords, we try to determine if there is a correlation between stock price and daily sentiment using an ARMA GARCH Model.
+There exist many social factors that contribute to this stock value but this paper aims to establish a methodology to test whether twitter sentiment is informative in predicting stock price movement and its volatility for the Chevron Corporation stock(CVX).
+This is done by using a DistilBert transformer architecture to assign a sentiment score for each tweet and afterwords, we try to determine if there is a correlation between stock price and daily sentiment using an ARMA GARCH Model.
 
@@
 Generally, this is influenced by factors such as market dynamics, economic conditions and changes to economic policy.
-Through this paper, we seek to determine whether this can be predicted or determined through observing public speculation on Twitter, the "virtual public square." Being able to determine whether there exists a correlation between public sentiment and the stock price might prove as a valuable indicator for many groups such as investors, activists, and companies officials to determine how much of a correlation a change in public opinion has to the stock value.
+Through this paper, we seek to determine whether this can be predicted or determined through observing public speculation on Twitter, the "virtual public square." Being able to determine whether public sentiment can be informative in predicting stock price might prove as a valuable indicator for many groups such as investors, activists, and companies officials to determine how much of a correlation a change in public opinion has to the stock value.
 %\paragraph{Review of the Literature}
@@
 \paragraph{}
-	In this paper, we will explore using a BERT Transformer model to generate sentiment scores of twitter data from the year 2021 and compare with the 2021 stock prices of the Chevron Corporation (CVX) to determine whether there exists any significant correlation.
+	In this paper, we will explore using a distilBERT Transformer model to generate sentiment scores of twitter data from the years 2021 and 2022, and comparing it to the stock prices of the Chevron Corporation (CVX) within the same period to determine whether there exists correlation.
 \paragraph{}
@@
 \paragraph{}
-	We use two datasets for this paper: topical twitter tweets from the year 2021 and historical stock data for CVX for the year 2021. 
+	For the period of 2021-2022,  CVX stock data and twitter tweets were collected for analysis.
 %%\paragraph{how the economic data was obtained}
 \paragraph{}
-	Gathering the Historic Stock data was the easiest part of the data collection process.
-The collection was done through Yahoo Finance's Historical Stock Data tool.
-The following is a plot of the highs and lows for the year 2021 generated using the matplotlib package for python \citep{Hunter_2007}.
+	Historic Stock data for the Chevron Corporation was collected using Yahoo Finance's Historical Stock Data tool.
+The following is a figure that shows the fluctuations of the Stock Highs, the Stock Lows and the Closing Prices over the observed period that was generated using the matplotlib package for python \citep{Hunter_2007}.
 
@@
   \includegraphics[width=\textwidth]{../figures/fig1.pdf}
-  \caption{Here we can see the fluctuations of the highs and lows for the stock price of CVX in 2021 with the highs labeled blue and the lows labeled yellow.
-In general both values tend to follow each other.}\label{fig:fig1}
+  \caption{A plot of historic CVX stock data from 2021 to 2022}\label{fig:fig1}
+  \end{center}
+\end{figure}
+
+\paragraph{}
+	While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the Closing Price and the Returns which can be taken by taking the log difference of the Closing Prices.
+
+\begin{figure}[!hb]
+  \begin{center}
+  \includegraphics[width=\textwidth]{../figures/fig2.pdf}
+  \caption{A plot of historic CVX stock data from 2021 to 2022 and the returns}\label{fig:fig2}
   \end{center}
@@
 	We also used the data processing library Pandas in order to generate summary statistics as shown below:
-
 \begin{table}[!hb]
@@
     \begin{tabular}{l|c|r} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
-      \textbf{Metrics} & \textbf{High} & \textbf{Low}\\
+      \textbf{Metrics} & \textbf{Close} & \textbf{Returns}\\
       \hline
-      count & 251.000000 & 251.000000\\
-      mean & 105.196175 & 103.091753\\
-      std & 7.747654 & 7.814207\\
-      min & 85.949997 & 83.889999\\
-      25\% & 99.900002 & 97.724998\\
-      50\% & 105.080002 & 102.970001\\
-      75\% & 110.330002 & 107.969998\\
-      max & 119.339996 & 118.040001\\
+      count & 503.000000 & 502.000000\\
+      mean & 131.520815 & 0.001496\\
+      std & 30.228298 & 0.018412\\
+      min & 84.709999	 & - 0.069374\\
+      25\% & 103.989998 & -0.008429\\
+      50\% & 118.790001 & 0.002891\\
+      75\% & 160.619995 & 0.013058\\
+      max & 188.050003 & 0.085292\\
     \end{tabular}
@@
 \paragraph{}
-	The range of the stock value goes from 83.889 to 119.336 and is representative of the stock prices from January 4th, 2021 to December 30th, 2021.
-There are 251 days that the stock data was available for in 2021.
-This is because Chevron is a part of the New York Stock Exchange which is closed all day on Saturdays, Sundays and nine holidays a year.
+	The range of the closing values for the observed period was 84.70 to 188.05; the lowest and highest values were observed on January 4th, 2021 November 15th, 2022.
+There are 502 days that the stock data was available for since Chevron is a part of the New York Stock Exchange which is closed all day on Saturdays, Sundays and nine holidays a year.
 This was something that was taken into consideration when working with twitter data.
@@
 In short, the process used to scrape the data was to first create some auxiliary functions for tasks such as determining how many tweets need to be gathered at a given time and create some functions to make it easier to pass in queries in the Twitter Search Scraper object.
-There are 2 things you can query for and that is by using either some topic keywords or the tweets from a specific user.
+Regarding the collection of tweets, the query can either be for some topic keywords or the tweets from a specific user.
 
 \paragraph{}
-	For the purpose of this paper, we scraped 5 tweets a day with the topic query "Chevron Oil" from January 1st 2021 to December 31st.
-We then saved all the 1825 generated tweets as a csv and merged them with the CVX stock data on the Date axis after matching datatypes.
+	For the purpose of this paper, 10 tweets were scraped with the topic query "CVX" from January 1st 2021 to December 31st 2022.
+7290 tweets were generated, saved as a csv and merged with the CVX stock data on the Date axis after matching datatypes.
 This also omitted tweets which were created when the stock market was closed in order to simplify the analysis.
-Using this we were able to perform sentiment and calculate correlation.
+Using this we were able to perform sentiment analysis and calculate correlation.
 
@@
 
-\subsection{Data Collection}
-Twitter data related to the Chevron Corporation was collected using web scraping techniques.
-Specifically, tweets containing the term "CVX" were extracted from Twitter using the topic selection method provided by the snscrape\citep{justanotherarchivist_2022} Python wrapper.
-The tweets were collected for a period of 2 years, from January 1, 2021 to December 31, 2022 with 10 tweets being collected each day.
-
 \subsection{Sentiment Analysis}
 \paragraph{The Transformer Model}
-	As we mentioned earlier, Transformers have shown a lot of promise, outperforming its competitors in speed and accuracy for natural language processing tasks.
+	As mentioned in the first section, Transformers models have shown a lot of promise for a variety of natural language processing tasks, outperforming its competitors in speed and accuracy.
 The BERT model seems to be particularly well suited for tasks of sentiment analysis.
-Transformers work based on the concept of "attention" which was introduced in "Attention is all you need" \citep{vaswani2017attention} is a deep learning model that was first used for computer vision models.
+Transformers work based on the concept of "attention" which was introduced in "Attention is all you need" \citep{vaswani2017attention} .
+Attention allows Transformers to learn the relationships between the words in a sentence or sequence of words.
+To do this, the Transformer splits the input sequence into tokens (usually individual words or sub-words) and embeds them into a high-dimensional vector space.
+It then applies multiple layers of self-attention, where each token in the sequence is given a weight based on its relevance to the other tokens.
+The self-attention mechanism allows the model to focus on the most important parts of the input sequence and learn dependencies between the words.
+After the self-attention layers, the Transformer applies feedforward neural networks to further refine the representations of the tokens.
 Transformers create differential weights signaling which words in a sentence are the most critical to further process.
-This allows them to "forget"  irrelevant information which would use other critical resources.
 
@@
 \end{tikzpicture}
-\caption{In this figure we can observe a very simplified version of the Transformer model with its two major components, the encoder and the decoder.
-The encoder processes a text input through a stack of transformer layers.
-In some situations, another set of transformer layers, the decoder, can be used to predict a target output.
-Note that this model might be used for a task such as language translation.\citep{devlin2018bert}}\label{fig:fig2}
+\caption{In this figure we can observe a very simplified version of the Transformer model with its two major components, the encoder and the decoder.\citep{devlin2018bert}}\label{fig:fig2}
 \end{figure}
+The Transformer architecture consists of two main components: an encoder and a decoder.The encoder takes in the input sequence and generates a sequence of hidden representations, which are then passed to the decoder.
+The decoder then uses the encoder's output to generate the final output sequence.
 
@@
 \paragraph{}
-We will be specifically using BERT-base which is a version of BERT with 12 transformation layers, and 768 Hidden Layers.\citep{muller_2022} This is more reasonable for the task we have at hand and we will implement this using the Hugging Face transformers package.
+We will be specifically using distil-BERT which is a version of BERT with 12 transformation layers, and 768 Hidden Layers.\citep{muller_2022} This is more reasonable for the task we have at hand and we will implement this using the Hugging Face transformers pipeline package\citep{huggingface2023}.
 For each day, the average sentiment score of all tweets was calculated.
@@
 Score is a numeric value from the range [0,1] where the higher the score the more confident the sentiment analyzed is correct.
-This variable is one of interest to us since we want to use it to measure correlation with highs of the stock market The summary statistics listed the following:
-
-\begin{table}[!hb]
-  \begin{center}
-    \caption{Summary Statistics for the Sentiment Analysis of Tweets}
-    \label{tab:table2}
-    \begin{tabular}{l|c|r} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
-      \textbf{Metrics} & \textbf{High} \\
-      \hline
-      count & 1160 \\
-      mean & 0.960652 \\
-      std & 0.086946 \\
-      min & 0.500485 \\
-      25\% & 0.9740872 \\
-      50\% & 0.992183 \\
-      75\% & 0.997086 \\
-      max & 0.999799 \\
-    \end{tabular}
-  \end{center}
-\end{table}
-
-\paragraph{}
-To calculate correlation, we must make sure that the fundamental assumptions are satisfied.
-The data is continuous and monotonic so we can proceed with Kendall's correlation.
-We used pandas to calculate Kendall's correlation.
-The following is a heat map of the correlation plotted using the seaborn package for python \citep{Waskom2021}.
+This score is the confidence that the model gives for the sentiment assignment and serves as a way to observe sentiment as a continuous variable.
+When combined and observed as a frequency histogram, it seems that the sentiment scores for the period are centered around a slightly positive value of 0.1 indicating sentiment for the CVX term was generally positive but normally distributed more or less.
 
@@
   \begin{center}
-  \includegraphics[width=\textwidth]{../figures/fig2.pdf}
-  \caption{Here we can observe the correlation between sentiment score and stock high price. The value is -0.009447. }\label{fig:fig2}
+  \includegraphics[width=\textwidth]{../figures/fig3.pdf}
+  \caption{Sentiment Distribution }\label{fig:fig2}
   \end{center}
@@
 
-Given that the correlation it is negative, this indicates that there is a very minor inverse relationship between score and stock price.
-But given how low it is, this result is practically negligible and it appears that there is almost 0 correlation between the variables we are measuring.
-This indicates a lot of revision being needed for the data and methods of analysis in this paper.
+\paragraph{}
+ARMA-GARCH models have several assumptions, including the stationarity of the time series data, the presence of autoregressive and moving average processes, the normality and lack of autocorrelation in the residuals, the constant conditional variance of the data, the absence of autoregressive conditional heteroscedasticity effects, and a sufficient sample size.
+These assumptions are important to ensure unbiased parameter estimates and accurate predictions.
+Some of these assumptions such as the normality and lack of autocorrelation in the residuals, the constant conditional variance of the data, the absence of autoregressive conditional heteroscedasticity effects were checked manually by making plots using R as such:
+\begin{figure}[!hb]
+  \begin{center}
+  \includegraphics[width=\textwidth]{../figures/fig4.pdf}
+  \caption{Garch Model Residuals}\label{fig:fig1}
+  \end{center}
+\end{figure}
+
+ and those that remained were checked by the rugarch\citep{rugarch}, readr\citep{readr}, forecast\citep{forecast}, tseries\citep{tseries}, garchx\citep{garchx}, and TSA\citep{TSA} packages.
+
+\paragraph{}
+In the analysis, an ARMA-GARCH model was first created only using the daily sentiment and then comparing to an ARMA-GARCH model with daily sentiment as an exogenous variable.
+The ARMA part of this technique, models the autocorrelation and moving average patterns in the data and GARCH models the volatility or conditional heteroskedasticity of the data.
+To determine whether daily sentiment, the exogenous variable has any effect on the model, we conducted the Likelihood ratio test.
+The log likelihood values for the base model and the model with sentiment as a variable are 1293.56 and 504.85, respectively.
+
+A higher log likelihood value indicates a better fit to the data.
+Therefore, based on the log likelihood values, the ARIMA(0,0,0) model with non-zero mean fits the returns better than the one which includes the sentiment score as an exogenous variable therefore, we could not reject the null hypothesis that the exogenous variable has no effect on the model.
+We tried this same technique by applying a weight to the sentiment score and obtained similar results.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \paragraph{}
-	As mentioned before, this paper is the first one to take the approach of using Transformers to determine whether it is possible to find out the correlation between Twitter Sentiment and Stock prices of prominent fossil fuel corporations.
+	As mentioned before, this paper is the first one to take the approach of using Transformers to determine whether twitter sentiment is informative in predicting the volatility of the stock price of the Chevron Corporation.
 In summary, this paper accomplished this task through the following:
@@
     \item Describing the results
-    Through code and analysis, we were eventually did get a correlation coefficient score of -0.009447 which is very low based on what was expected indicating that there is very little correlation between twitter sentiment and stock price.
 
 \end{itemize}
-\paragraph{}
-	In its current state, this study is intended to work as a proof of concept to determine whether it is possible to create a data processing pipeline which could be used to assign sentiment scores and connect it to stock time series data so the results determined through this preliminary paper should not be taken as a final answer to the research question that were posed.
-This study had many limitations which can be addressed to get a more accurate answer.
+\paragraph{Possible Expansions}
+	One possible expansion of this study would be to increase the sample size to include more observations and thus increase the robustness of the analysis.
+This would allow for more accurate statistical tests and a better understanding of the relationship between sentiment and stock price movement/volatility.
+Another possible expansion would be to test for causality using techniques like the Granger causality test, which would allow us to determine whether sentiment scores are truly predictive of stock price movements or whether they are just correlated.
+Additionally, conducting a meta-analysis of multiple companies in the fossil fuel industry or across multiple industries could provide broader insights into the relationship between sentiment and stock prices.
 
-	For instance the transformer pipeline model that was used handled cleaning and preprocessing automatically, this might have lead to improper tokenization which allowed for incorrect sentiment analysis.
-The 18th tweet in merged.csv reads
+\paragraph{Takeaways}
+Although this study found that both weighted and unweighted sentiment scores may not have been effective in predicting stock price movement and volatility of CVX, it established a novel methodology for analyzing Twitter sentiment data and determining whether it is informative in predicting stock prices.
+This methodology can be applied to other industries and sectors to gain a better understanding of the role that sentiment plays in stock price movements.
+The methodology can be useful for multiple groups, such as Public Relations departments in companies like Chevron, who can use this to assess the effectiveness of their publicity campaigns on the company's valuation, leading to higher profits and public influence.
+Alternatively, environmental groups can use this methodology to measure the effectiveness of their activism campaigns in influencing the trading power of Chevron Stock ownership.
+This methodology provides a way for various groups to adjust their strategies to influence public sentiment and in turn stock value.
 
-	"Richmond Mayor Tom Butt was publicly optimistic about a Chevron oil refinery spill. In private he took on a much different tone."
-
-	This was labelled as positive by BERT but in actuality this is a negative tweet.
-\paragraph{}
-	To avoid instances like this we could also use more terms for the tweet querying such as a specific event such as an oil spill or possibly the stock indicator itself.
-
-\paragraph{}
-The major things to address as next steps are improving the data quality, quantity and analysis.
-I will also explore using the twitter API to gather tweets instead of using snscrape since the API is the prefered method of gathering tweets in professional contexts and this opens data gathering up to many more possibilities with new methods and feature information that could be gathered using the API query feature.
-Having more tweets per day is also beneficial in improving the quality of analysis.
-
-\paragraph{}
-Furthermore, using different data and methods would allow us to possibly create a model that can forecast stock pricing if the correlation is strong enough.
-This would be done in a manner similarly to \citep{zhao2019forecasting}.
-
-This project will require much more development and expansion before a conclusion  can be determined but analyzing the effect of public sentiment on stock prices of fossil fuel companies can provide valuable insight into how public opinion can be used to augment or reduce the effects of climate change.
+\paragraph{Conclusion}
+Overall, this study provides valuable insights into the use of Twitter sentiment analysis as a tool for predicting stock prices, and points towards potential avenues for further research.
+With further research, determined but analyzing the effect of public sentiment on stock prices of fossil fuel companies can provide valuable insight into how public opinion can be used to augment or reduce the effects of climate change.
 \bigskip

### 2023-04-20 code/Thesis_R_Code.Rmd
saved r code

@@
 summary(arma_model)
+output_path <- "/Users/pranavtavildar/Desktop/Senior-Thesis/figures/fig4.pdf"
+
+pdf(file = output_path)
 residuals_garch <- residuals(garch_model)
@@
 sentiment_df = sentiment_df[-1,]
+
+output_path <- "/Users/pranavtavildar/Desktop/Senior-Thesis/figures/fig3.pdf"
+
+pdf(file = output_path)
 hist(sentiment_df$sentiment, main = "Sentiment Distribution", xlab = "Sentiment Score", ylab = "Frequency")
-
-output_path <- "/Users/pranavtavildar/Desktop/Senior-Thesis/FrontiersPoster/FrontiersPoster_files/poster_files/figures/sentimenthist.png"
-
-png(file = output_path)
 dev.off()

### 2023-04-21 manuscript/manuscript.tex
quick comments

@@
 \author{Pranav Tavildar\\
+  University of Connecticut \\
+  Advisor: Jun Yan\\
+  Department of Statistics\\
   University of Connecticut
@@
 
+\jy{alphabetical; no repeating words in title. Read my writing tips and practice them}
 \bigskip
@@
 
+\jy{what do I recommend for linewidth?}
+
+\jy{Two figure labels are multiply defined. Read the log and fix the warnings}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\paragraph{Overview of topic}
-\paragraph{}
+
 The Chevron Corporation is an America-based energy company thats has operations in over 180 countries where it has vertically integrated all operations in its supply chain such as exploration, production, refinement, chemical manufacturing, transportation, sales, marketing, and power generation.
@@
 As of when this paper was written, the Chevron Corporation has the 11th highest market capitalization with 361.57 billion dollars in traded stocks.
-	\paragraph{}
+
 As a publicly traded company, Chevron's stock price is determined by supply and demand in the market.
@@
 %\paragraph{Review of the Literature}
-\paragraph{}
+
 To quantify public opinion, this paper uses a machine learning technique known as sentiment analysis \citep{medhat2014sentiment} which uses natural language processing to determine whether the sentiment towards any subject is positive or negative and assigns it a score.
-\paragraph{}
+
  Some papers in the literature use this technique in relation to analyzing activity in the stock market.
@@
 Furthermore, Lu-Tao Zhao and Guan-Rong Zheng web text and applied Sentiment Analysis in order to do Oil Price forecasting \citep{zhao2019forecasting}.
-This concept has also been applied in order to predict one step ahead of the closing price of the stock market in Thailand using a hybrid model composed of Principle Component Analysis (PCA) for Data Processing (Dimensionality Reduction), Empirical Mode Distribution (EMD) for signal interpretation and data preprocessing, and the Long-Short-Term-Memory(LSTM) model, a specialized type of recurrent neural network for the sentiment analysis.
-\citep{srijiranon2022hybrid}
-\paragraph{}
+This concept has also been applied in order to predict one step ahead of the closing price of the stock market in Thailand using a hybrid model composed of Principle Component Analysis (PCA) for Data Processing (Dimensionality Reduction), Empirical Mode Distribution (EMD) for signal interpretation and data preprocessing, and the Long-Short-Term-Memory(LSTM) model, a specialized type of recurrent neural network for the sentiment analysis \citep{srijiranon2022hybrid}.
+
 While these methods have been tried and proven, as of writing this, the preferred method of analyzing sequence data for most natural language processing is through the use of transformer models.
 This type of model was first introduced in the paper "Attention is all you need" \citep{vaswani2017attention}.
-\paragraph{}
+
 This model sought to improve the problems existing with the Recurrent Neural Network(RNN) model which used to be the preferred model for language processing tasks.
@@
 %\paragraph{My Contribution}
-\paragraph{}
+
 In this paper, we will explore using a distilBERT Transformer model to generate sentiment scores of twitter data from the years 2021 and 2022, and comparing it to the stock prices of the Chevron Corporation (CVX) within the same period to determine whether there exists correlation.
-\paragraph{}
+
 This following is a roadmap for this study: 1) Describing the Data, 2) Explaining the Statistical Methods and the Machine Learning Concepts, 3) Explaining the Results of our Paper, 4) Conducting Discussion of this Study
@@
 \section{Data Description}
-\paragraph{}
+
 For the period of 2021-2022,  CVX stock data and twitter tweets were collected for analysis.
 %%\paragraph{how the economic data was obtained}
-\paragraph{}
+
 Historic Stock data for the Chevron Corporation was collected using Yahoo Finance's Historical Stock Data tool.
 The following is a figure that shows the fluctuations of the Stock Highs, the Stock Lows and the Closing Prices over the observed period that was generated using the matplotlib package for python \citep{Hunter_2007}.
+
+\jy{the figure x-labels are cutoff}
 
@@
 
-\paragraph{}
 While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the Closing Price and the Returns which can be taken by taking the log difference of the Closing Prices.
 
+\jy{The upper panel is repeating. Only keep one.}
 \begin{figure}[!hb]
@@
 
-\paragraph{}
+\jy{Use table styles from my template}
 We also used the data processing library Pandas in order to generate summary statistics as shown below:
@@
 
-\paragraph{}
 The range of the closing values for the observed period was 84.70 to 188.05; the lowest and highest values were observed on January 4th, 2021 November 15th, 2022.
@@
 
-\paragraph{}
 The twitter data was scraped using the python package snscrape \citep{justanotherarchivist_2022}.
@@
 
-\paragraph{}
 For the purpose of this paper, 10 tweets were scraped with the topic query "CVX" from January 1st 2021 to December 31st 2022.
@@
 
-\begin{figure}[H]
+\begin{figure}[tbp]
 \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
@@
 \end{tikzpicture}
-\caption{In this figure we can observe a very simplified version of the Transformer model with its two major components, the encoder and the decoder.\citep{devlin2018bert}}\label{fig:fig2}
+\caption{In this figure we can observe a very simplified version of the Transformer model with its two major components, the encoder and the decoder \citep{devlin2018bert}.}
+\label{fig:fig2}
 \end{figure}
@@
 
-\paragraph{}
 We will be utilizing Bidirectional Encoder Representations from Transformers (BERT) for our sentiment analysis.
@@
 
-\paragraph{}
 This model was initially trained on Wikipedia and Google’s BooksCorpus which contain 2,500,000,000 words and 800,000,000 words respectively.
@@
 
-\paragraph{}
 We will be specifically using distil-BERT which is a version of BERT with 12 transformation layers, and 768 Hidden Layers.\citep{muller_2022} This is more reasonable for the task we have at hand and we will implement this using the Hugging Face transformers pipeline package\citep{huggingface2023}.
@@
 \section{Results}
-\paragraph{}
+
 The sentiment analysis took approximately 12 minutes to run and the data generated created 3 new columns in the working dataframe: sentiment, label, and score.
@@
 
-\begin{figure}[H]
+\begin{figure}[tbp]
   \begin{center}
@@
 
-\paragraph{}
 ARMA-GARCH models have several assumptions, including the stationarity of the time series data, the presence of autoregressive and moving average processes, the normality and lack of autocorrelation in the residuals, the constant conditional variance of the data, the absence of autoregressive conditional heteroscedasticity effects, and a sufficient sample size.
@@
 Some of these assumptions such as the normality and lack of autocorrelation in the residuals, the constant conditional variance of the data, the absence of autoregressive conditional heteroscedasticity effects were checked manually by making plots using R as such:
+
+\jy{reference to figures/tables by their labels. Never H or h. Always tbp for floating locations.}
 \begin{figure}[!hb]
@@
 
+\jy{a blank line means a new paragraph}
+
 and those that remained were checked by the rugarch\citep{rugarch}, readr\citep{readr}, forecast\citep{forecast}, tseries\citep{tseries}, garchx\citep{garchx}, and TSA\citep{TSA} packages.
+\jy{space before citep}
 
-\paragraph{}
 In the analysis, an ARMA-GARCH model was first created only using the daily sentiment and then comparing to an ARMA-GARCH model with daily sentiment as an exogenous variable.
@@
 \section{Discussion}
-\paragraph{}
+
 As mentioned before, this paper is the first one to take the approach of using Transformers to determine whether twitter sentiment is informative in predicting the volatility of the stock price of the Chevron Corporation.
@@
     \item Describing the data and the methods by which the data was obtained.
-    \item Describing the methods behind the sentiment analysis and correlation derivation
-    \item Describing the results
+    \item Describing the methods behind the sentiment analysis and correlation derivation.
+    \item Describing the results.
+\end{itemize}
 
-\end{itemize}
+\jy{close figure/table captions with a period.}
+
+\jy{no need for paragraph titles}
 \paragraph{Possible Expansions}
@@
 With further research, determined but analyzing the effect of public sentiment on stock prices of fossil fuel companies can provide valuable insight into how public opinion can be used to augment or reduce the effects of climate change.
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
+
+\jy{no manually controlled spacing}
+
 \bibliographystyle{chicago}

### 2023-04-25 manuscript/manuscript.tex
changed

@@
 As a publicly traded company, the Chevron Corporation has the 11th highest market capitalization in the world with 361.57 billion dollars in traded stocks.
-There exist many social factors that contribute to this stock value but this paper aims to establish a methodology to test whether twitter sentiment is informative in predicting stock price movement and its volatility for the Chevron Corporation stock(CVX).
+There exist many social factors that contribute to this stock value but this paper aims to establish a methodology to test whether public opinion in social media is informative in predicting stock price movement and its volatility for the Chevron Corporation stock(CVX).
 This is done by using a DistilBert transformer architecture to assign a sentiment score for each tweet and afterwords, we try to determine if there is a correlation between stock price and daily sentiment using an ARMA GARCH Model.
@@
 \jy{alphabetical; no repeating words in title. Read my writing tips and practice them}
+%% did this
 \bigskip
@@
 \jy{what do I recommend for linewidth?}
-
+%% need the ebook
 \jy{Two figure labels are multiply defined. Read the log and fix the warnings}
+%% could not find the figures
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \jy{the figure x-labels are cutoff}
-
+%%% fixed this
 \begin{figure}[!hb]
@@
 While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the Closing Price and the Returns which can be taken by taking the log difference of the Closing Prices.
+sample
 
 \jy{The upper panel is repeating. Only keep one.}
+%%%fixed this part
 \begin{figure}[!hb]
@@
 \jy{Use table styles from my template}
+%%% Need link to the efor,
 We also used the data processing library Pandas in order to generate summary statistics as shown below:
@@
 
-\jy{reference to figures/tables by their labels. Never H or h. Always tbp for floating locations.}
+\jy{reference to figures/tables by their labels. Never H or h. Always tbp for floating locations. }
+%% Confused
 \begin{figure}[!hb]
@@
 
-and those that remained were checked by the rugarch\citep{rugarch}, readr\citep{readr}, forecast\citep{forecast}, tseries\citep{tseries}, garchx\citep{garchx}, and TSA\citep{TSA} packages.
+and those that remained were checked by the rugarch \citep{rugarch}, readr \citep{readr}, forecast \citep{forecast}, tseries \citep{tseries}, garchx \citep{garchx}, and TSA \citep{TSA} packages.
 \jy{space before citep}
+%%did it
 
@@
     \item Describing the results.
-\end{itemize}
+\end{itemize}.
 
 \jy{close figure/table captions with a period.}
+%%think I did it but not sure
 
 \jy{no need for paragraph titles}
-\paragraph{Possible Expansions}
+%%done
+\paragraph{}
 One possible expansion of this study would be to increase the sample size to include more observations and thus increase the robustness of the analysis.
@@
 
-\paragraph{Takeaways}
+\paragraph{}
 Although this study found that both weighted and unweighted sentiment scores may not have been effective in predicting stock price movement and volatility of CVX, it established a novel methodology for analyzing Twitter sentiment data and determining whether it is informative in predicting stock prices.
@@
 
-\paragraph{Conclusion}
+\paragraph{}
 Overall, this study provides valuable insights into the use of Twitter sentiment analysis as a tool for predicting stock prices, and points towards potential avenues for further research.

### 2023-04-26 manuscript/manuscript.tex
Fixed the Results Section and added formatting

@@
 
-\jy{alphabetical; no repeating words in title. Read my writing tips and practice them}
+%%\jy{alphabetical; no repeating words in title. Read my writing tips and practice them}
 %% did this
@@
 
-\jy{what do I recommend for linewidth?}
+%%\jy{what do I recommend for linewidth?}
 %% need the ebook
-\jy{Two figure labels are multiply defined. Read the log and fix the warnings}
+%%\jy{Two figure labels are multiply defined. Read the log and fix the warnings}
 %% could not find the figures
@@
 Historic Stock data for the Chevron Corporation was collected using Yahoo Finance's Historical Stock Data tool.
-The following is a figure that shows the fluctuations of the Stock Highs, the Stock Lows and the Closing Prices over the observed period that was generated using the matplotlib package for python \citep{Hunter_2007}.
+Figure ~\ref{fig:stockdata} shows the fluctuations of the Stock Highs, the Stock Lows and the Closing Prices over the observed period that was generated using the matplotlib package for python \citep{Hunter_2007}.
 
-\jy{the figure x-labels are cutoff}
+%%\jy{the figure x-labels are cutoff}
 %%% fixed this
-\begin{figure}[!hb]
+\begin{figure}[tbp]
   \begin{center}
   \includegraphics[width=\textwidth]{../figures/fig1.pdf}
-  \caption{A plot of historic CVX stock data from 2021 to 2022}\label{fig:fig1}
+  \caption{A plot of historic CVX stock data from 2021 to 2022.}\label{fig:stockdata}
   \end{center}
@@
 While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the Closing Price and the Returns which can be taken by taking the log difference of the Closing Prices.
-sample
 
-\jy{The upper panel is repeating. Only keep one.}
+%%\jy{The upper panel is repeating. Only keep one.}
 %%%fixed this part
-\begin{figure}[!hb]
+\begin{figure}[tbp]
   \begin{center}
   \includegraphics[width=\textwidth]{../figures/fig2.pdf}
-  \caption{A plot of historic CVX stock data from 2021 to 2022 and the returns}\label{fig:fig2}
+  \caption{A plot of historic CVX stock data from 2021 to 2022 and the returns.}\label{fig:returns}
   \end{center}
@@
 
-\jy{Use table styles from my template}
+%%\jy{Use table styles from my template}
 %%% Need link to the efor,
-We also used the data processing library Pandas in order to generate summary statistics as shown below:
-\begin{table}[!hb]
+We also used the data processing library Pandas in order to generate summary statistics as shown in Table~\ref{tab:sumstat}
+\begin{table}[tbp]
   \begin{center}
-    \caption{Summary Statistics for the Chevron Stock data}
-    \label{tab:table1}
+    \caption{Summary Statistics for the Chevron Stock Data.}
+    \label{tab:sumstat}
     \begin{tabular}{l|c|r} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
@@
 \end{tikzpicture}
-\caption{In this figure we can observe a very simplified version of the Transformer model with its two major components, the encoder and the decoder \citep{devlin2018bert}.}
-\label{fig:fig2}
+\caption{In this figure we can observe a very simplified version of the Transformer model with its two major components, the encoder and the decoder. \citep{devlin2018bert}.}
+\label{fig:transformer}
 \end{figure}
@@
   \includegraphics[width=\textwidth]{../figures/fig3.pdf}
-  \caption{Sentiment Distribution }\label{fig:fig2}
+  \caption{Sentiment Distribution Histogram.}\label{fig:sentimenthist}
   \end{center}
@@
 These assumptions are important to ensure unbiased parameter estimates and accurate predictions.
-Some of these assumptions such as the normality and lack of autocorrelation in the residuals, the constant conditional variance of the data, the absence of autoregressive conditional heteroscedasticity effects were checked manually by making plots using R as such:
+Some of these assumptions such as the normality and lack of autocorrelation in the residuals, the constant conditional variance of the data, the absence of autoregressive conditional heteroscedasticity effects were checked manually by making plots using R shown in Figure~\ref{fig:garchvar}
 
-\jy{reference to figures/tables by their labels. Never H or h. Always tbp for floating locations. }
-%% Confused
-\begin{figure}[!hb]
+%%\jy{reference to figures/tables by their labels. Never H or h. Always tbp for floating locations. }
+\begin{figure}[tbp]
   \begin{center}
   \includegraphics[width=\textwidth]{../figures/fig4.pdf}
-  \caption{Garch Model Residuals}\label{fig:fig1}
+  \caption{Garch Model Residuals.}\label{fig:garchvar}
   \end{center}
@@
 
-\jy{a blank line means a new paragraph}
-
-and those that remained were checked by the rugarch \citep{rugarch}, readr \citep{readr}, forecast \citep{forecast}, tseries \citep{tseries}, garchx \citep{garchx}, and TSA \citep{TSA} packages.
-\jy{space before citep}
+%%\jy{space before citep}
 %%did it
 
-In the analysis, an ARMA-GARCH model was first created only using the daily sentiment and then comparing to an ARMA-GARCH model with daily sentiment as an exogenous variable.
-The ARMA part of this technique, models the autocorrelation and moving average patterns in the data and GARCH models the volatility or conditional heteroskedasticity of the data.
-To determine whether daily sentiment, the exogenous variable has any effect on the model, we conducted the Likelihood ratio test.
-The log likelihood values for the base model and the model with sentiment as a variable are 1293.56 and 504.85, respectively.
+%%% we conducted a z-test on the basis of coefficient
+%%% arima two log-liklihoods, should be similar
+%%% do the same thing with garch
+In this analysis, we constructed an ARMA-GARCH model using daily sentiment data and compared it to a model that included daily sentiment as an exogenous variable.
+The ARMA part of the model captures the autocorrelation and moving average patterns in the data, while the GARCH part models the volatility or conditional heteroskedasticity of the data.
+To investigate whether daily sentiment as an exogenous variable has any effect on the model, we conducted z-tests to determine whether the addition of this new variable had a significant effect on the ARMA-GARCH model.
 
-A higher log likelihood value indicates a better fit to the data.
-Therefore, based on the log likelihood values, the ARIMA(0,0,0) model with non-zero mean fits the returns better than the one which includes the sentiment score as an exogenous variable therefore, we could not reject the null hypothesis that the exogenous variable has no effect on the model.
-We tried this same technique by applying a weight to the sentiment score and obtained similar results.
+We first performed a z-test for the parameters of the ARMA portion.
+The null hypothesis was that the addition of the exogenous variable would have no effect on the ARMA part of the original model, meaning the coefficient of xreg (the sentiment score) is 0.
+We found the difference between the estimated coefficient in the armax model (0.0015) and the hypothesized value of zero and divided it by the standard error of the coefficient (0.004), which gave us a z-score of 0.375.
+The corresponding p-value was 0.35383, which is much larger than our chosen significance level of 0.05.
+Thus, we could not reject the null hypothesis that the addition of this exogenous variable has a significant effect on the means and autocorrelation of this model.
+The log-likelihood values for the ARMA portion were calculated by the \texttt{arimax} package so to further test this hypothesis, we did the log-liklihood ratio test for the ARMA portion of the model.
+The log likelihood values for the base model and the model with sentiment as a variable are 1293.56 and 1293.98, respectively.
+A higher log likelihood value by a factor of 2 times indicates a better fit to the data but the differences between the likelihood scores are not nearly significant enough of a difference to allow us to reject the null hypothesis.
+
+Afterwards we followed the same process for the GARCH portion.
+In this portion, the null hypothesis for the z test is that the addition of this exogenous variable would have no effect on the GARCH part of the original model.
+The estimated coefficient for this portion was 9.931742e-11  and the estimated standard error was 1.542782e-03.
+This gives a z-score critical value of 6.43755372e-8 which has a p-value that's almost 1 which is very large compared to chosen significance value of 0.05.
+This means that we could not reject the null hypothesis that the addition of this exogenous variable has a significant effect on the variance and volatility of this model.
+
+Overall, our tests suggest that the twitter sentiment scores from our sampling methods for the period of 2021 to 2022 are not effective in predicting the volatility and autocorrelation of the CVX stock.
 
@@
     \item Describing the results.
-\end{itemize}.
+\end{itemize}
 
-\jy{close figure/table captions with a period.}
-%%think I did it but not sure
+%\jy{close figure/table captions with a period.}
+%%did
 
-\jy{no need for paragraph titles}
 %%done
-\paragraph{}
 One possible expansion of this study would be to increase the sample size to include more observations and thus increase the robustness of the analysis.
@@
 
-\paragraph{}
 Although this study found that both weighted and unweighted sentiment scores may not have been effective in predicting stock price movement and volatility of CVX, it established a novel methodology for analyzing Twitter sentiment data and determining whether it is informative in predicting stock prices.
@@
 
-\paragraph{}
 Overall, this study provides valuable insights into the use of Twitter sentiment analysis as a tool for predicting stock prices, and points towards potential avenues for further research.
@@
 
-\jy{no manually controlled spacing}
+%%%\jy{no manually controlled spacing}
 

### 2023-04-27 manuscript/manuscript.tex
edits and comments

@@
 \title{Sentiment Analysis of Twitter in Relation to Fossil Fuel Stock Prices}
-\author{Pranav Tavildar\\
-  University of Connecticut \\
-  Advisor: Jun Yan\\
+\author{Pranav Tavildar\\[2ex]
+  Advisor: Jun Yan\\[2ex]
   Department of Statistics\\
@@
 As a publicly traded company, the Chevron Corporation has the 11th highest market capitalization in the world with 361.57 billion dollars in traded stocks.
-There exist many social factors that contribute to this stock value but this paper aims to establish a methodology to test whether public opinion in social media is informative in predicting stock price movement and its volatility for the Chevron Corporation stock(CVX).
+There exist many social factors that contribute to this stock value but this paper aims to establish a methodology to test whether public opinion in social media is informative in predicting stock price movement and its volatility for the Chevron Corporation stock (CVX).
 This is done by using a DistilBert transformer architecture to assign a sentiment score for each tweet and afterwords, we try to determine if there is a correlation between stock price and daily sentiment using an ARMA GARCH Model.
 
-%%\jy{alphabetical; no repeating words in title. Read my writing tips and practice them}
-%% did this
 \bigskip
@@
 chevron;
-twitter;
-nlp;
-sentiment analysis.
-
+sentiment analysis;
+twitter.
 \end{abstract}
 
-%%\jy{what do I recommend for linewidth?}
-%% need the ebook
-%%\jy{Two figure labels are multiply defined. Read the log and fix the warnings}
-%% could not find the figures
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec: intro}
+\jy{don't put space in labels}
 %\paragraph{Overview of topic}
@@
 Generally, this is influenced by factors such as market dynamics, economic conditions and changes to economic policy.
-Through this paper, we seek to determine whether this can be predicted or determined through observing public speculation on Twitter, the "virtual public square." Being able to determine whether public sentiment can be informative in predicting stock price might prove as a valuable indicator for many groups such as investors, activists, and companies officials to determine how much of a correlation a change in public opinion has to the stock value.
+Through this paper, we seek to determine whether this can be predicted or determined through observing public speculation on Twitter, the ``virtual public square." Being able to determine whether public sentiment can be informative in predicting stock price might prove as a valuable indicator for many groups such as investors, activists, and companies officials to determine how much of a correlation a change in public opinion has to the stock value.
 %\paragraph{Review of the Literature}
 
-To quantify public opinion, this paper uses a machine learning technique known as sentiment analysis \citep{medhat2014sentiment} which uses natural language processing to determine whether the sentiment towards any subject is positive or negative and assigns it a score.
-
- Some papers in the literature use this technique in relation to analyzing activity in the stock market.
+Sentiment analysis \citep{medhat2014sentiment} is a tool which uses natural language processing to determine whether the sentiment towards any subject is positive or negative and assigns it a score.
+It has been used to analyze activity in the stock market.
 Koosha Golmohammadi and Osmar R.
-Zaiane for instance use sentiment analysis with Twitter data to improve their Contextual Anomaly Detection(CAD) model in order to detect Market Manipulation in the United States and Canada \citep{golmohammadi2017sentiment}.
+Zaiane for instance use sentiment analysis with Twitter data to improve their Contextual Anomaly Detection (CAD) model in order to detect Market Manipulation in the United States and Canada \citep{golmohammadi2017sentiment}.
 Furthermore, Lu-Tao Zhao and Guan-Rong Zheng web text and applied Sentiment Analysis in order to do Oil Price forecasting \citep{zhao2019forecasting}.
@@
 
-While these methods have been tried and proven, as of writing this, the preferred method of analyzing sequence data for most natural language processing is through the use of transformer models.
-This type of model was first introduced in the paper "Attention is all you need" \citep{vaswani2017attention}.
-
+A popular method of analyzing sequence data for most natural language processing is through the use of transformer models  \citep{vaswani2017attention}.
 This model sought to improve the problems existing with the Recurrent Neural Network(RNN) model which used to be the preferred model for language processing tasks.
@@
 
-In this paper, we will explore using a distilBERT Transformer model to generate sentiment scores of twitter data from the years 2021 and 2022, and comparing it to the stock prices of the Chevron Corporation (CVX) within the same period to determine whether there exists correlation.
+In this paper, we will explore using a distilBERT Transformer model to generate sentiment scores of twitter data from the years 2021 and 2022, and investigate its association with the stock prices of the Chevron Corporation (CVX) within the same period.
 
-This following is a roadmap for this study: 1) Describing the Data, 2) Explaining the Statistical Methods and the Machine Learning Concepts, 3) Explaining the Results of our Paper, 4) Conducting Discussion of this Study
+\jy{refer to sections by their labels}
+
+This following is a roadmap for this study: 1) Describing the Data, 2) Explaining the Statistical Methods and the Machine Learning Concepts, 3) Explaining the Results of our Paper, 4) Conducting Discussion of this Study.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Data Description} \jy{put section labels within the sections}
 \label{sec: datadesc}
-\section{Data Description}
+
+\jy{Merge those paragraphs that are overally small.}
 
 For the period of 2021-2022,  CVX stock data and twitter tweets were collected for analysis.
-%%\paragraph{how the economic data was obtained}
-
 Historic Stock data for the Chevron Corporation was collected using Yahoo Finance's Historical Stock Data tool.
@@
 
-While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the Closing Price and the Returns which can be taken by taking the log difference of the Closing Prices.
+While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the closing Price and the Returns which can be taken by taking the log difference of the closing Prices.
 
@@
 
+\jy{make sure every figure/table is referred to in the text}
+
 %%\jy{Use table styles from my template}
 %%% Need link to the efor,
-We also used the data processing library Pandas in order to generate summary statistics as shown in Table~\ref{tab:sumstat}
+
 \begin{table}[tbp]
@@
     \label{tab:sumstat}
-    \begin{tabular}{l|c|r} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
-      \textbf{Metrics} & \textbf{Close} & \textbf{Returns}\\
-      \hline
+    \begin{tabular}{lcr} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
+      \toprule
+      {Metrics} & {Close} & {Returns}\\
+      \midrule
       count & 503.000000 & 502.000000\\
@@
       max & 188.050003 & 0.085292\\
+      \bottomrule
     \end{tabular}
@@
 
+We also used the data processing library Pandas in order to generate summary statistics as shown in Table~\ref{tab:sumstat}
 The range of the closing values for the observed period was 84.70 to 188.05; the lowest and highest values were observed on January 4th, 2021 November 15th, 2022.
@@
 
-For the purpose of this paper, 10 tweets were scraped with the topic query "CVX" from January 1st 2021 to December 31st 2022.
+For the purpose of this paper, 10 tweets were scraped with the topic query ``CVX" from January 1st 2021 to December 31st 2022.
 7290 tweets were generated, saved as a csv and merged with the CVX stock data on the Date axis after matching datatypes.
@@
 The BERT model seems to be particularly well suited for tasks of sentiment analysis.
-Transformers work based on the concept of "attention" which was introduced in "Attention is all you need" \citep{vaswani2017attention} .
+Transformers work based on the concept of ``attention" which was introduced in ``Attention is all you need" \citep{vaswani2017attention} .
 Attention allows Transformers to learn the relationships between the words in a sentence or sequence of words.
@@
 
-We will be specifically using distil-BERT which is a version of BERT with 12 transformation layers, and 768 Hidden Layers.\citep{muller_2022} This is more reasonable for the task we have at hand and we will implement this using the Hugging Face transformers pipeline package\citep{huggingface2023}.
+\jy{put negative signs in math mode}
+
+We will be specifically using distil-BERT which is a version of BERT with 12 transformation layers, and 768 Hidden Layers \citep{muller_2022}.
+This is more reasonable for the task we have at hand and we will implement this using the Hugging Face transformers pipeline package \citep{huggingface2023}.
 For each day, the average sentiment score of all tweets was calculated.
-Sentiment scores range from -1 to 1, where -1 represents a very negative sentiment and 1 represents a very positive sentiment.
+Sentiment scores range from $-1$ to 1, where -1 represents a very negative sentiment and 1 represents a very positive sentiment.
 
-\subsection{ARMA-GARCH Modeling}
-The daily returns for Chevron's stock (CVX) were obtained from calculating as the daily logarithmic difference of the closing prices.
+\subsection{ARMA GARCH Modeling}
+The daily returns for CVX were obtained from calculating as the daily logarithmic difference of the closing prices.
 ARMA-GARCH modeling was then performed to investigate the relationship between the daily returns and the sentiment scores.
@@
   \includegraphics[width=\textwidth]{../figures/fig3.pdf}
-  \caption{Sentiment Distribution Histogram.}\label{fig:sentimenthist}
+  \caption{Sentiment histogram.}\label{fig:sentimenthist}
   \end{center}
@@
 
-%%\jy{reference to figures/tables by their labels. Never H or h. Always tbp for floating locations. }
+\jy{make the label of the vertical axis more informative}
 \begin{figure}[tbp]
@@
   \includegraphics[width=\textwidth]{../figures/fig4.pdf}
-  \caption{Garch Model Residuals.}\label{fig:garchvar}
+  \caption{Garch model residuals.}\label{fig:garchvar}
   \end{center}
@@
 
-%%\jy{space before citep}
-%%did it
-
-%%% we conducted a z-test on the basis of coefficient
-%%% arima two log-liklihoods, should be similar
-%%% do the same thing with garch
 In this analysis, we constructed an ARMA-GARCH model using daily sentiment data and compared it to a model that included daily sentiment as an exogenous variable.
@@
 
-Overall, our tests suggest that the twitter sentiment scores from our sampling methods for the period of 2021 to 2022 are not effective in predicting the volatility and autocorrelation of the CVX stock.
+Overall, our tests suggest that the twitter sentiment scores from our sampling methods for the period of 2021 to 2022 are not effective in predicting the mean nor the volatility of the CVX stock.
 
@@
 \begin{itemize}
-    \item Introducing some background behind the Chevron Corporation and Sentiment Analysis as a Practice.
+    \item Introducing some background behind the Chevron Corporation and sentiment analysis as a practice.
     \item Describing the data and the methods by which the data was obtained.
@@
 
-%\jy{close figure/table captions with a period.}
-%%did
-
-%%done
 One possible expansion of this study would be to increase the sample size to include more observations and thus increase the robustness of the analysis.

### 2023-04-27 manuscript/manuscript.tex
Fixed requested Edits

@@
 \section{Introduction}
-\label{sec: intro}
-\jy{don't put space in labels}
+\label{sec:intro}
+%%\jy{don't put space in labels}
 %\paragraph{Overview of topic}
@@
 
-\jy{refer to sections by their labels}
+%%%\jy{refer to sections by their labels}
+%%completed
 
-This following is a roadmap for this study: 1) Describing the Data, 2) Explaining the Statistical Methods and the Machine Learning Concepts, 3) Explaining the Results of our Paper, 4) Conducting Discussion of this Study.
+This following is a roadmap for this study: Section \ref{sec:intro}: Introducing Concepts and Providing Background, Section \ref{sec:datadesc}: Describing the Data , Section \ref{sec:methods}: Explaining the Statistical Methods and the Machine Learning Concepts, Section \ref{sec:results}: Explaining the Results of our Paper, and Section \ref{sec:discussion}: Conducting Discussion of this Study.
 
@@
 
-\section{Data Description} \jy{put section labels within the sections}
-\label{sec: datadesc}
+\section{Data Description} 
+\label{sec:datadesc}
+%%\jy{put section labels within the sections}
 
-\jy{Merge those paragraphs that are overally small.}
+%%\jy{Merge those paragraphs that are overally small.}
 
@@
 Figure ~\ref{fig:stockdata} shows the fluctuations of the Stock Highs, the Stock Lows and the Closing Prices over the observed period that was generated using the matplotlib package for python \citep{Hunter_2007}.
-
+While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the closing Price and the Returns which can be taken by taking the log difference of the closing Prices, refer to Figure~{fig:returns}.
 %%\jy{the figure x-labels are cutoff}
@@
 \end{figure}
-
-While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the closing Price and the Returns which can be taken by taking the log difference of the closing Prices.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\label{sec: methods}
 \section{Methods}
+\label{sec:methods}
 
@@
 The decoder then uses the encoder's output to generate the final output sequence.
+Figure~\ref{fig:transformer} is a simple layout of this architecture
 
@@
 
-\jy{put negative signs in math mode}
+%%\jy{put negative signs in math mode}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\label{sec: results}
 \section{Results}
+\label{sec:results}
 
@@
 
-\jy{make the label of the vertical axis more informative}
+%%\jy{make the label of the vertical axis more informative}
 \begin{figure}[tbp]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\label{sec: discussion}
 \section{Discussion}
+\label{sec:discussion}
 

### 2023-04-27 code/Arma_garch.R

@@ -28,7 +28,8 @@ garch_model
 
 summary(arma_model)
 residuals_garch <- residuals(garch_model)
-plot(residuals_garch)
+plot(residuals_garch, ylab = "Residuals as Percentage", xlab = "Time", 
+     main = "GARCH Residuals Plot")
 
 #### To do this part (sentiment score is an exogenous variable) through the following https://rdrr.io/cran/TSA/man/arimax.html
 ### Find the ARMA mean but if this fails look at the GARCH portion using the following https://www.rdocumentation.org/packages/garchx/versions/1.3/topics/garchx

### 2023-04-27 manuscript/manuscript.tex
Final Version Before Review

@@
 
-The Chevron Corporation is an America-based energy company thats has operations in over 180 countries where it has vertically integrated all operations in its supply chain such as exploration, production, refinement, chemical manufacturing, transportation, sales, marketing, and power generation.
-A lot of revenue comes from these streams but they also receive funding from government subsidies and stock revenue.
+The Chevron Corporation is an energy company based in the United States thats has operations in over 180 countries where it has vertically integrated all operations in its supply chain such as exploration, production, refinement, chemical manufacturing, transportation, sales, marketing, and power generation.
+A lot of revenue comes from these streams but the corporation also receives funding from government subsidies and stock revenue.
 As of when this paper was written, the Chevron Corporation has the 11th highest market capitalization with 361.57 billion dollars in traded stocks.
@@
 Due to its novelty and its promising qualities, many are applying Transformers for various tasks, yet nobody has this used this approach to find out whether it is possible to find out the correlation between Twitter Sentiment and Stock prices of prominent fossil fuel corporations.
-In this paper, we specifically will focus on the Chevron Corporation (though in future iterations, we might extend this to multiple corporations in this field).
 %\paragraph{My Contribution}
@@
 
-This following is a roadmap for this study: Section \ref{sec:intro}: Introducing Concepts and Providing Background, Section \ref{sec:datadesc}: Describing the Data , Section \ref{sec:methods}: Explaining the Statistical Methods and the Machine Learning Concepts, Section \ref{sec:results}: Explaining the Results of our Paper, and Section \ref{sec:discussion}: Conducting Discussion of this Study.
+This following is a roadmap for this study: Section \ref{sec:intro}: Introducing Concepts and Providing Background, Section \ref{sec:datadesc}: Describing the Data, Section \ref{sec:methods}: Explaining the Statistical Methods and the Machine Learning Concepts, Section \ref{sec:results}: Explaining the Results of our Paper, and Section \ref{sec:discussion}: Conducting Discussion of this Study.
 
@@
 Figure ~\ref{fig:stockdata} shows the fluctuations of the Stock Highs, the Stock Lows and the Closing Prices over the observed period that was generated using the matplotlib package for python \citep{Hunter_2007}.
-While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the closing Price and the Returns which can be taken by taking the log difference of the closing Prices, refer to Figure~{fig:returns}.
+While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the closing Price and the Returns which can be taken by taking the log difference of the closing Prices, refer to Figure~\ref{fig:returns}.
 %%\jy{the figure x-labels are cutoff}
@@
 
-\jy{make sure every figure/table is referred to in the text}
+%%%\jy{make sure every figure/table is referred to in the text}
 
@@
 
-We also used the data processing library Pandas in order to generate summary statistics as shown in Table~\ref{tab:sumstat}
+We also used the data processing library Pandas in order to generate summary statistics as shown in Table~\ref{tab:sumstat}.
 The range of the closing values for the observed period was 84.70 to 188.05; the lowest and highest values were observed on January 4th, 2021 November 15th, 2022.
@@
 
-For the purpose of this paper, 10 tweets were scraped with the topic query ``CVX" from January 1st 2021 to December 31st 2022.
+For the purpose of this paper, 10 tweets were scraped daily with the topic query ``CVX" from January 1st 2021 to December 31st 2022.
 7290 tweets were generated, saved as a csv and merged with the CVX stock data on the Date axis after matching datatypes.
@@
 The BERT model seems to be particularly well suited for tasks of sentiment analysis.
-Transformers work based on the concept of ``attention" which was introduced in ``Attention is all you need" \citep{vaswani2017attention} .
+Transformers work based on the concept of ``attention" which was introduced in ``Attention is all you need" \citep{vaswani2017attention}.
 Attention allows Transformers to learn the relationships between the words in a sentence or sequence of words.
@@
 The decoder then uses the encoder's output to generate the final output sequence.
-Figure~\ref{fig:transformer} is a simple layout of this architecture
+Figure~\ref{fig:transformer} is a simple representation of this architecture that takes into account its key components.
 
@@
 
+Similarly, z-tests were conducted for weighted sentiment as the exogenous variable and the null hypothesis was still rejected with p values of 0.476 and 1 for the ARMA and GARCH portions respectively.
+
 Overall, our tests suggest that the twitter sentiment scores from our sampling methods for the period of 2021 to 2022 are not effective in predicting the mean nor the volatility of the CVX stock.

### 2023-04-28 manuscript/manuscript.tex
final edits

@@
 
-Although this study found that both weighted and unweighted sentiment scores may not have been effective in predicting stock price movement and volatility of CVX, it established a novel methodology for analyzing Twitter sentiment data and determining whether it is informative in predicting stock prices.
-This methodology can be applied to other industries and sectors to gain a better understanding of the role that sentiment plays in stock price movements.
-The methodology can be useful for multiple groups, such as Public Relations departments in companies like Chevron, who can use this to assess the effectiveness of their publicity campaigns on the company's valuation, leading to higher profits and public influence.
+While this study did not find weighted and unweighted sentiment scores to be effective in predicting stock price movements and volatility of CVX, it introduced a novel approach to analyzing Twitter sentiment data and evaluating its predictive value for stock prices.
+This methodology can be applied in other industries and sectors to gain a better understanding of the role that sentiment plays in stock price movements.
+The methodology can be helpful to various groups, such as Public Relations departments in companies like Chevron, who can use this to assess the effectiveness of their publicity campaigns on the company's valuation, leading to higher profits and public influence.
 Alternatively, environmental groups can use this methodology to measure the effectiveness of their activism campaigns in influencing the trading power of Chevron Stock ownership.
@@
 Overall, this study provides valuable insights into the use of Twitter sentiment analysis as a tool for predicting stock prices, and points towards potential avenues for further research.
-With further research, determined but analyzing the effect of public sentiment on stock prices of fossil fuel companies can provide valuable insight into how public opinion can be used to augment or reduce the effects of climate change.
 

### 2023-05-14 manuscript/manuscript.tex
Final Commit: Negative values are in math mode and all fig referenced

@@
 For each day, the average sentiment score of all tweets was calculated.
-Sentiment scores range from $-1$ to 1, where -1 represents a very negative sentiment and 1 represents a very positive sentiment.
+Sentiment scores range from $-1$ to 1, where $-1$ represents a very negative sentiment and 1 represents a very positive sentiment.
 
@@
 This score is the confidence that the model gives for the sentiment assignment and serves as a way to observe sentiment as a continuous variable.
-When combined and observed as a frequency histogram, it seems that the sentiment scores for the period are centered around a slightly positive value of 0.1 indicating sentiment for the CVX term was generally positive but normally distributed more or less.
+When combined and observed as a frequency histogram as in Figure~/ref{fig:sentimenthist}, it seems that the sentiment scores for the period are centered around a slightly positive value of 0.1 indicating sentiment for the CVX term was generally positive but normally distributed more or less.
 

### 2023-05-14 manuscript/manuscript.tex
Final Commit, all figs are referenced

@@
 This score is the confidence that the model gives for the sentiment assignment and serves as a way to observe sentiment as a continuous variable.
-When combined and observed as a frequency histogram as in Figure~/ref{fig:sentimenthist}, it seems that the sentiment scores for the period are centered around a slightly positive value of 0.1 indicating sentiment for the CVX term was generally positive but normally distributed more or less.
+When combined and observed as a frequency histogram as in Figure~\ref{fig:sentimenthist}, it seems that the sentiment scores for the period are centered around a slightly positive value of 0.1 indicating sentiment for the CVX term was generally positive but normally distributed more or less.
 
